---
title: "Ritu Project — Data Management"
author: "Tianqi Ouyang"
date: "2026-04-09"
execute:
  eval: true
  warning: false
  message: false
---

> **Ritu cohort — Local/Early stage only.** This pipeline is the Jiaxuan data
> management pipeline with one added exclusion: all **advanced/metastatic**
> patients (`tumor_stage == "Advanced/Metastatic"`, stage III–IV) are removed at
> the end of Section 5.16, leaving **N = 323** (190 carboplatin, 133 cisplatin).
> Every variable definition, formula, window and exclusion above that step is
> unchanged. The analytic dataset is written to `ritu_final_master.rds`.
>
> REDCap inputs are read from `../Data/` because this project lives in a
> `Ritu project/` subfolder alongside the Jiaxuan project; the RPDR `.txt`
> pull is read from its original absolute path.

# 1 Variable Name Dictionary

Variables with the same name as the PDF / REDCap CSV are not listed. Only **renamed** and **newly created** variables are shown.

## 1.1 Renamed Variables

| PDF / REDCap | In Code |
|---|---|
| `bl_date` | `baseline_sample_date` |
| `fu_date` | `last_follow_up_date` |
| `baseline_creatinine` | `baseline_cre` |
| `cys_c_baseline` | `baseline_cys_c` |
| `er_status_90d` | `ed_status_90d` |
| `er_visit_date` | `ed_visit_date` |
| `er_visit_diff` | `ed_visit_diff` |
| `other_ed_visit` | `other_ed` |
| `hosp_visit_diff` | `hosp_visit_0_diff` |
| `hosp_visit_reason___1–11` | `hosp_visit_0_reason_1–11` |

## 1.2 Labeled REDCap Variables

These variables are stored as numeric codes in the REDCap CSV and labeled in section 5.7.

| In Code | REDCap Coding |
|---|---|
| `sex` | 1=Male, 2=Female |
| `race` | 1=White, 2=Black, 3=Asian, 4=Other, 5=Unknown |
| `ethnicity` | 1=Non-Hispanic, 2=Hispanic, 3=Unknown |
| `tumor_stage` | 1=Local/neoadjuvant/early (stage I–II), 2=Advanced/metastatic (stage III–IV). **Ritu cohort keeps code 1 only** |
| `platin_group` | 1=Carboplatin, 2=Cisplatin, 3=Unknown |
| `ecog_score` | REDCap stores 1=ECOG 0, 2=ECOG 1, …, 7=N/A. Remapped to actual ECOG (0–5); 7 → NA |
| `ecog_estimate` | Same remapping as `ecog_score`; shown only when `ecog_score` = N/A |

## 1.3 Derived — eGFR & Kidney Function

| In Code | Description |
|---|---|
| `ckd_epi_gfr_cre_cys` | CKD-EPI 2012 combined creatinine + cystatin C eGFR (mL/min/1.73m²) |
| `ckd_epi_gfr_cre_cys_unindex` | Combined CKD-EPI eGFR adjusted for body surface area (mL/min) |
| `baseline_cre_egfr_unindexed` | CKD-EPI creatinine eGFR adjusted for body surface area (mL/min) |
| `baseline_cys_c_egfr_unindexed` | CKD-EPI cystatin C eGFR adjusted for body surface area (mL/min) |

## 1.4 Derived — RPDR Pre-baseline Labs (within 45 days before baseline)

| In Code | RPDR Group_Id | Units |
|---|---|---|
| `pre_CRE_45days` | `CRE` | mg/dL |
| `pre_HGB_45days` | `HGB` | g/dL |
| `pre_PLT_45days` | `PLT` | ×10³/µL |
| `pre_ALB_45days` | `ALB` | g/dL |
| `pre_GHBA1C_45days` | `GHBA1C` | % |

## 1.5 Derived — Exposure

| In Code | Description |
|---|---|
| `cr_cys` | Creatinine-to-cystatin C ratio: `baseline_cre / baseline_cys_c` |
| `cr_cys_7` | Primary exposure (binary): 1 if `cr_cys` < 0.7, 0 otherwise |
| `cr_cys_cat` | 4-level categorical: <0.5 / 0.5–0.7 / 0.7–0.9 / ≥0.9 |
| `exposure_epi_30` | Binary: 1 if cystatin C eGFR < 0.7 × creatinine eGFR (CKD-EPI based) |

## 1.6 Derived — Adverse Events (within 90 days of baseline)

| In Code | Description |
|---|---|
| `Anemia_g2_90days` | Binary: 1 if HGB < 8 g/dL within 90 days (CTCAE grade ≥ 2) |
| `Anemia_g3_90days` | Binary: 1 if HGB < 6.5 g/dL within 90 days (CTCAE grade ≥ 3) |
| `Throm_g2_90days` | Binary: 1 if PLT < 75 ×10³/µL within 90 days (CTCAE grade ≥ 2) |
| `Throm_g3_90days` | Binary: 1 if PLT < 50 ×10³/µL within 90 days (CTCAE grade ≥ 3) |
| `AKI_g2_90days` | Binary: 1 if creatinine > 1.5× pre-baseline within 90 days (CTCAE grade ≥ 2) |
| `AKI_g3_90days` | Binary: 1 if creatinine > 3× pre-baseline within 90 days (CTCAE grade ≥ 3) |
| `AKI_kdigo_90days` | Binary: 1 if CRE ≥ 1.5× pre-baseline OR ≥ 0.3 mg/dL increase within any 2-day window, within 90 days (KDIGO) |
| `grade_2_aes` | Composite binary: 1 if any of anemia/throm/AKI grade ≥ 2 |
| `grade_3_aes` | Composite binary: 1 if any of anemia/throm/AKI grade ≥ 3 |
| `time_to_anemia_2` … `time_to_aki_3` | Days from baseline to each AE (90 if no event) |
| `time_to_grade_2_aes` / `time_to_grade_3_aes` | Days to earliest composite AE (min across anemia/throm/AKI) |

## 1.7 Derived — Hospitalizations & ED

Hospitalization reasons 1–11 per REDCap codebook:
1=Nausea/vomiting/GI, 2=Failure to thrive/fatigue/dehydration, 3=AKI,
4=Electrolyte abnormalities, 5=Cytopenia, 6=Febrile neutropenia,
7=Infection/sepsis, 8=Cancer progression, 9=Immune-related AE,
10=Planned surgery/port, 11=Other

| In Code | Description |
|---|---|
| `event_hosp_1` … `event_hosp_11` | Binary: 1 if hospitalized for that reason within 90 days |
| `time_to_event_hosp_1` … `time_to_event_hosp_11` | Days from baseline to hospitalization by reason (90 if none) |
| `event_hosp_immune_other` | Binary: 1 if hospitalised for Immune-related AE (`hosp_9`) OR Other (`hosp_11`) |
| `time_to_event_hosp_immune_other` | Earliest of `time_to_event_hosp_9` and `time_to_event_hosp_11` (90 if neither occurred) |
| `side_effect` | Binary: 1 if any hospitalization for reasons 1–7 (platinum-related AEs) |
| `time_to_side_effect` | Days to first platinum-related hospitalization (90 if none) |
| `extra_ed_n` | Count of additional ED visits (beyond the first) |
| `extra_hosp_n` | Count of additional hospitalizations (beyond the first) |

## 1.8 Derived — Mortality

| In Code | Description |
|---|---|
| `days_last_follow_up` | Days from baseline to last follow-up date |
| `death_90` | Binary: 1 if died within 90 days (REDCap `pt_status` = 3 "Dead") |
| `time_to_death_90` | Days to death, capped at 90 (90 if alive/censored) |
| `time_to_death_90_status` | 0=censored (alive at last follow-up), 2=dead within 90 days |

## 1.9 Derived — Comorbidities & Categories

| In Code | Description |
|---|---|
| `score` | Charlson comorbidity index weighted score (from RPDR ICD codes via `comorbidity` package) |
| `cci` | Charlson category: "mild" (score 1–2), "moderate" (3–4), "severe" (≥5) |
| `thyroid` | Binary: 1 if thyroid disease in RPDR diagnoses or medications |
| `smoking` | Binary: 1 if smoking/tobacco use in RPDR diagnoses |
| `steroids` | Binary: 1 if corticosteroid dispensed within 30 days before baseline |
| `hiv_rpdr` | Binary: 1 if HIV in RPDR diagnoses or medications |
| `bmi` | Body mass index: weight(kg) / height(m)² |
| `bmi_cat` | 1=Underweight (<18.5), 2=Normal (18.5–25), 3=Overweight (25–30), 4=Obese (≥30) |
| `age_cat` | 1=≤65 years, 2=66–80 years, 3=>80 years |
| `ici` | Binary: 1 if receiving immune checkpoint inhibitor (Atezolizumab, Pembrolizumab, or Durvalumab) |
| `cancer_type_cat_7` | Factor from `tumor_type`: Thoracic(1), Breast(2), GI(3,4), GU(5), GYN(7), HEENT(8), Other(6,9) |

## 1.10 Derived — Platinum Dosing

| In Code | Description |
|---|---|
| `carbo` | Binary: 1 if `platin_group` = Carboplatin |
| `cis` | Binary: 1 if `platin_group` = Cisplatin |
| `carbo_AUC` | Carboplatin AUC (from `platin_dose` for carboplatin patients; NA for cisplatin) |
| `cis_dose` | Cisplatin dose in mg/m² (from `platin_dose` for cisplatin patients; NA for carboplatin) |
| `high_dose` | Binary factor: 1=High-dose (carbo AUC ≥ 5 OR cisplatin ≥ 75 mg/m²), 0=Low-dose |
| `carbo_AUC_cat` | Carboplatin AUC category: "<3" or ">=3" |
| `cis_dose_cat` | Cisplatin dose category: 1=<75 mg/m², 2=≥75 mg/m², 0=not cisplatin |
| `cis_dose_high` | Cisplatin dose factor: "<75" or ">=75" (NA for non-cisplatin) |
| `cis_group` | Cisplatin dose tier: 1=<40 mg/m², 2=40–60 mg/m², 3=≥60 mg/m² |

## 1.11 Derived — Carboplatin Dose Discrepancy

Carboplatin is dosed via the **Calvert formula**: Dose(mg) = target AUC × (GFR + 25).
The actual administered dose is in REDCap. CKD-EPI Cr-Cys eGFR predicts what the dose
should be — the discrepancy between actual and predicted may relate to adverse outcomes.

| In Code | Description |
|---|---|
| `carbo_dose_redcap` | Actual administered carboplatin dose (mg) from REDCap |
| `carbo_dose_cre_cys` | Predicted dose (mg) from CKD-EPI Cr-Cys: AUC × (eGFR Cr-Cys unindexed + 25) |
| `dose_discrepancy` | Actual − predicted (mg): `carbo_dose_redcap − carbo_dose_cre_cys` |
| `dose_diff_pct` | (actual − predicted) / predicted × 100 (%) |
| `dd_gt25` | Binary factor: 1 if dose_discrepancy > 25 mg, 0 otherwise |
| `dd_gt50` | Binary factor: 1 if dose_discrepancy > 50 mg, 0 otherwise |
| `ecog_score_cat2` | ECOG binary: "0" vs ">=1" |
| `bmi_30` | BMI binary: "<30" vs ">=30" |
| `age_70` | Age binary: "<70" vs ">=70" |

## 1.12 Derived — Drug Indicators & Competing Risk

Drug indicators (binary 0/1) parsed from `regimen_dose` text by `create_drug_indicators()`:
`Bevacizumab`, `Paclitaxel`, `Pemetrexed`, `Durvalumab`, `Doxorubicin`,
`Pembrolizumab`, `Etoposide`, `Gemcitabine`, `Atezolizumab`, `Pertuzumab`,
`Trastuzumab`, `Docetaxel`, `Fluorouracil`, `Methotrexate`, `Vinblastine`,
`Administered_alone` (1 if no co-administered drugs detected),
`other_chemo` (1 if any of `Fluorouracil`, `Methotrexate`, `Vinblastine`)

Competing risk variables: `cmp_time_<outcome>` / `cmp_status_<outcome>` for each outcome.
Status coding: 0=censored (alive, no event by 90 days), 1=event occurred, 2=death (competing event)

---

# 2 Setup & Libraries

```{r}
#| label: setup
#| include: false
# Force UTF-8 locale so kable captions and other strings render real Unicode
# (e.g. em-dash) instead of <U+2014> escape sequences.
invisible(Sys.setlocale("LC_ALL", "en_US.UTF-8"))
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#| label: libraries
rm(list = ls())
library(readxl)
library(openxlsx)
library(dplyr)
library(tidyverse)
library(tableone)
library(writexl)
library(gtsummary)
library(survival)
library(ggplot2)
library(ggpubr)
library(splines)
library(lattice)
library(mice)
library(DescTools)
library(survminer)
library(finalfit)
library(tidycmprsk)
library(ggsurvfit)
library(comorbidity)
library(readr)
library(cowplot)
library(scales)
```

---

# 3 Functions (all from Copy 709)

Each function is defined in its own labeled cell.

## 3.1 standardize_colnames

```{r}
#| label: fn-standardize-colnames
standardize_colnames <- function(df) {
  # Replace non-alphanumeric characters with underscore
  names(df) <- gsub("[^[:alnum:]_]", "_", names(df))

  # Reduce multiple underscores to a single underscore
  names(df) <- gsub("_+", "_", names(df))

  # Remove underscore if it's at the end of the name
  names(df) <- gsub("_$", "", names(df))

  # Return the cleaned dataframe
  return(df)
}
```

## 3.2 create_events_and_times_1_11

Creates `event_hosp_1`–`event_hosp_11` and `time_to_event_hosp_1`–`time_to_event_hosp_11`
from `hosp_visit_0_*` (baseline) and extra `hosp_visit_1_*`–`hosp_visit_5_*` rows.

```{r}
#| label: fn-create-events-and-times-1-11
create_events_and_times_1_11 <- function(data) {
    # Initialize hospital event and time variables
    for (i in 1:11) {
        data[[paste0("event_hosp_", i)]] <- 0
        data[[paste0("time_to_event_hosp_", i)]] <- NA
    }

    # Process each row
    for (i in seq_len(nrow(data))) {
        # If baseline hospital visit is missing, set all to 0/NA
        if (is.na(data[i, "hosp_visit_0_diff"])) {
            for (j in 1:11) {
                data[i, paste0("event_hosp_", j)] <- 0
                data[i, paste0("time_to_event_hosp_", j)] <- NA
            }
        } else {
            # Baseline hospital visit
            for (j in 1:11) {
                if (!is.na(data[i, paste0("hosp_visit_0_reason_", j)]) &&
                    data[i, paste0("hosp_visit_0_reason_", j)] == 1) {
                    data[i, paste0("event_hosp_", j)] <- 1
                    data[i, paste0("time_to_event_hosp_", j)] <- data[i, "hosp_visit_0_diff"]
                }
            }
        }

        # Additional hospital visits
        if (!is.na(data[i, "other_hosp"]) && data[i, "other_hosp"] == 1) {
            extra_hosp_n <- as.numeric(data[i, "extra_hosp_n"])
            if (!is.na(extra_hosp_n) && extra_hosp_n > 0) {
                for (visit in 1:extra_hosp_n) {
                    for (j in 1:11) {
                        if (!is.na(data[i, paste0("event_hosp_", j)]) &&
                            data[i, paste0("event_hosp_", j)] == 0 &&
                            !is.na(data[i, paste0("hosp_visit_", visit, "_reason_", j)]) &&
                            data[i, paste0("hosp_visit_", visit, "_reason_", j)] == 1) {
                            data[i, paste0("event_hosp_", j)] <- 1
                            data[i, paste0("time_to_event_hosp_", j)] <- data[i, paste0("hosp_visit_", visit, "_diff")]
                        }
                    }
                }
            }
        }
    }

    return(data)
}
```

## 3.3 create_drug_indicators

Parses `regimen_dose` free text to create 0/1 indicators per co-drug.
`Administered_alone` = 1 when none of the 15 drugs are present.

```{r}
#| label: fn-create-drug-indicators
create_drug_indicators <- function(data) {

  # Create indicator for Bevacizumab
  data$Bevacizumab <- ifelse(grepl("Bevacizumab|Avastin", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Paclitaxel
  data$Paclitaxel <- ifelse(grepl("Paclitaxel|Taxol|Abraxane", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Pemetrexed
  data$Pemetrexed <- ifelse(grepl("Pemetrexed|pem\\b", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Durvalumab
  data$Durvalumab <- ifelse(grepl("Durvalumab|Durva", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Doxorubicin
  data$Doxorubicin <- ifelse(grepl("Doxorubicin|Adriamycin", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Pembrolizumab
  data$Pembrolizumab <- ifelse(grepl("Pembrolizumab|Pembro", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Etoposide
  data$Etoposide <- ifelse(grepl("Etoposide|etop\\b", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Gemcitabine
  data$Gemcitabine <- ifelse(grepl("Gemcitabine|\\bGem\\b", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Atezolizumab
  data$Atezolizumab <- ifelse(grepl("Atezolizumab", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Pertuzumab
  data$Pertuzumab <- ifelse(grepl("Pertuzumab", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Trastuzumab
  data$Trastuzumab <- ifelse(grepl("Trastuzumab|Traztuzumab|Transtuzumab|Herceptin",
                                   data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Docetaxel
  data$Docetaxel <- ifelse(grepl("Docetaxel|Taxotere", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Fluorouracil
  data$Fluorouracil <- ifelse(grepl("Fluorouracil|5FU", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Methotrexate
  data$Methotrexate <- ifelse(grepl("Methotrexate", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Vinblastine
  data$Vinblastine <- ifelse(grepl("Vinblastine", data$regimen_dose, ignore.case = TRUE), 1, 0)

  # Create indicator for Administered alone (absence of all the above drugs)
  all_drugs <- c("Bevacizumab", "Paclitaxel", "Pemetrexed", "Durvalumab", "Doxorubicin",
                 "Pembrolizumab", "Etoposide", "Gemcitabine", "Atezolizumab", "Pertuzumab",
                 "Trastuzumab", "Docetaxel", "Fluorouracil", "Methotrexate", "Vinblastine")

  data$Administered_alone <- ifelse(rowSums(data[, all_drugs]) == 0, 1, 0)

  # Other chemotherapy: any of Fluorouracil / Methotrexate / Vinblastine, i.e.
  # the partner drugs not already broken out individually in Table 1.
  data$other_chemo <- ifelse(
    data$Fluorouracil == 1 | data$Methotrexate == 1 | data$Vinblastine == 1,
    1, 0
  )

  return(data)
}
```

## 3.4 cmp_variable

Builds competing-risk time and status for a single outcome.
Status coding: 0 = censored, 1 = event occurred, 2 = death (competing event).
If death occurs first, the death time and status (0/2) override the event.

```{r}
#| label: fn-cmp-variable
cmp_variable <- function(data, event_time, event_status, name) {
  # Enquote the time and status variables to allow their evaluation within the data context
  event_time <- enquo(event_time)
  event_status <- enquo(event_status)


  # Create dynamic names for the new columns
  cmp_time_name <- paste0("cmp_time_", name)
  cmp_status_name <- paste0("cmp_status_", name)

  # Add new columns to the dataset using mutate()
  data %>%
    mutate(
      !!cmp_time_name := ifelse(time_to_death_90 <= !!event_time ,time_to_death_90,!!event_time),
      !!cmp_status_name := ifelse(time_to_death_90 <= !!event_time,time_to_death_90_status,!!event_status)
    )
}
```

## 3.5 pre_lab

Finds the **closest lab value on or before** `index_date` within the time window.
Returns one row per patient (most recent qualifying lab result).

> See **Section 6.1** for the bug found in Jiaxuan's version of this function
> and how Copy 709 correctly implements it.

```{r}
#| label: fn-pre-lab
###### pre lab  index data included closest date
pre_lab <- function(data, month, time, index_date, Group_Id) {
  index_date <- enquo(index_date)
  if (month) {
    time_value <- time * 30
  } else {
    time_value <- time
  }


  lab_name <- paste0("pre_", Group_Id, "_", time_value, "days")
  lab_date_name <- paste0("pre_", Group_Id, "_", time_value, "days_date")

  result <- data %>%
    filter(Group_Id == !!Group_Id, grepl("^\\d+\\.\\d+$", Result)) %>%
    filter(!is.na(Result)) %>%
    mutate(Result = as.numeric(Result)) %>%
    filter(Seq_Date_Time >= (!!index_date) - time_value, Seq_Date_Time <= !!index_date) %>%
    arrange(EMPI, desc(Seq_Date_Time)) %>%
    distinct(EMPI, .keep_all = TRUE) %>%
    rename(!!lab_name := Result,
           !!lab_date_name := Seq_Date_Time) %>%
    select(EMPI,
           !!lab_name, !!lab_date_name)

  return(result)
}
```

## 3.6 post_lab_less_than_cutpoint

Finds the **first post-baseline lab value below a clinical cutpoint** within `days`.
Used for post-baseline lab cutpoint outcomes.

```{r}
#| label: fn-post-lab-less-than-cutpoint
## post lab cutoff function
post_lab_less_than_cutpoint <- function(data,days,index_date,Group_ID,Group_ID_name,outcome_name,cutpoint) {
  index_date <- enquo(index_date)
  lab_name <- paste0("post_", Group_ID_name, "_cutpoint_", days, "days")
  lab_date_name <- paste0("post_", Group_ID_name, "_cutpoint_", days, "days_date")

  result <- data %>%
    filter(Group_Id %in% Group_ID) %>%
    filter(grepl("^[><]?\\d+\\.?\\d* ?$",Result)) %>%
    mutate(Result=as.numeric(parse_number(Result))) %>%
    filter(!is.na(Result)) %>%
    filter(Seq_Date_Time > (!!index_date), Seq_Date_Time <= !!index_date + days) %>%
    filter(Result<cutpoint) %>%
    arrange(EMPI,Seq_Date_Time) %>%
    distinct(EMPI, .keep_all = TRUE) %>%
    rename(!!lab_name := Result,
           !!lab_date_name := Seq_Date_Time) %>%
    select(EMPI,
           !!lab_name, !!lab_date_name)
  return(result)
}
```

## 3.7 dia_list_name

Identifies patients with a given diagnosis (and optionally medication) on or before
`index_date`. Supports excluding specific diagnosis name strings.

```{r}
#| label: fn-dia-list-name
dia_list_name <- function(data, listed_names, index_date, excluded_names = NULL, med_data = NULL, med_names = NULL) {
  #
  if (!is.null(excluded_names)) {
    excluded_pattern <- paste(
      gsub("([][()])", "\\\\\\1", excluded_names),  #
      collapse = "|"
    )
  }

  if (is.null(excluded_names)) {
    dia_result <- data %>%
      filter(Date <= {{index_date}}) %>%
      filter(grepl(paste(listed_names, collapse = "|"), Diagnosis_Name, ignore.case = TRUE)) %>%
      distinct(EMPI)
  } else {
    dia_result <- data %>%
      filter(Date <= {{index_date}}) %>%
      filter(
        grepl(paste(listed_names, collapse = "|"), Diagnosis_Name, ignore.case = TRUE),
        !grepl(excluded_pattern, Diagnosis_Name, ignore.case = TRUE)  #
      ) %>%
      distinct(EMPI)
  }

  if (!is.null(med_data)) {
    med_result <- med_data %>%
      filter(Medication_Date <= {{index_date}}) %>%
      filter(grepl(paste(med_names, collapse = "|"), Medication, ignore.case = TRUE)) %>%
      distinct(EMPI)
  } else {
    med_result <- NULL
  }

  final_result <- rbind(dia_result, med_result) %>%
    distinct(EMPI)

  return(final_result)
}
```

---

# 4 Data Loading

## 4.1 REDCap export

```{r}
#| label: load-redcap
master <- read_csv('../Data/CystatinCInPatientsO_DATA_2026-04-27_0819.csv')

whole_cohort <- read_csv('../Data/Included Patients WHOLE cohort.csv')

# Rename empi to EMPI (uppercase for RPDR compatibility)
master <- master %>% rename(EMPI = empi)

# Keep only patients whose EMPI appears in the whole cohort list
master <- master %>% filter(EMPI %in% whole_cohort$EMPI)
```

## 4.2 Standardise column names, rename ED / hosp variables

```{r}
#| label: load-standardize-rename
master <- standardize_colnames(master)

# Rename ED variables: PDF uses er_* prefix → code uses ed_*
# Rename hosp_visit_* → hosp_visit_0_* (baseline) and other_hosp_* → hosp_visit_*
master <- master %>%
   rename(ed_visit_diff  = er_visit_diff,
          ed_visit_date  = er_visit_date,
          ed_status_90d  = er_status_90d,
          other_ed       = other_ed_visit) %>%
  rename_with(~ gsub("^hosp_visit_", "hosp_visit_0_", .x), starts_with("hosp_visit_")) %>%
  rename_with(~ gsub("^other_hosp_", "hosp_visit_", .x), starts_with("other_hosp_")) %>%
  rename_with(~ gsub("_visit", "", .x) %>%
                gsub("_(\\d+)_", "_\\1_reason_", .), starts_with("other_ed_visit_")) %>%
  rename_with(~ gsub("^ed_visit_", "ed_visit_0_", .x), starts_with("ed_visit_")) %>%
  rename_with(~ gsub("^other_ed_", "ed_visit_", .x), starts_with("other_ed_")) %>%
  mutate(other_hosp = ifelse(other_hosp != 1 | is.na(other_hosp), 0, 1),
         other_ed   = ifelse(other_ed   != 1 | is.na(other_ed),   0, 1),
         extra_hosp_n = ifelse(other_hosp == 1,
                               rowSums(across(hosp_extra_1:hosp_extra_5), na.rm = TRUE), 0),
         extra_ed_n   = ifelse(other_ed == 1,
                               rowSums(across(ed_extra_1:ed_extra_3)), 0))
```

## 4.3 Create hospitalization event / time variables (reasons 1–11)

```{r}
#| label: load-hosp-events
master <- create_events_and_times_1_11(master)
```

## 4.4 Create platinum-related side_effect variable (hosp reasons 1–7)

```{r}
#| label: load-side-effect
# side_effect = 1 if any of hosp reasons 1–7 (platinum-associated AEs) occurred
side_effect <- master %>%
  select(record_id, matches("^event_hosp_[1-7]$|^time_to_event_hosp_[1-7]$")) %>%
  rowwise() %>%
  mutate(
    side_effect = if_else(any(c_across(starts_with("event_hosp_")) == 1, na.rm = TRUE), 1, 0),
    time_to_side_effect = {
      if (side_effect == 1) {
        times <- c_across(starts_with("time_to_event_hosp_"))[c_across(starts_with("event_hosp_")) == 1]
        if (any(!is.na(times))) min(times, na.rm = TRUE) else NA_real_
      } else {
        NA_real_
      }
    }
  ) %>%
  ungroup() %>% select(record_id, side_effect, time_to_side_effect)

# Censor at 90 days
side_effect <- side_effect %>% mutate(
  side_effect = case_when(
    side_effect == 1 & time_to_side_effect > 90 ~ 0,
    TRUE ~ side_effect
  ),
  time_to_side_effect = case_when(
    side_effect == 1 & time_to_side_effect > 90 ~ 90,
    side_effect == 0 ~ 90,
    TRUE ~ time_to_side_effect
  )
)
```

## 4.4b Create overall hospitalization variable (any reason 1–11)

```{r}
#| label: load-overall-hosp
# any_hosp = 1 if hospitalized for ANY reason (1–11) within 90 days
overall_hosp <- master %>%
  select(record_id, matches("^event_hosp_\\d+$"), matches("^time_to_event_hosp_\\d+$")) %>%
  rowwise() %>%
  mutate(
    any_hosp = if_else(any(c_across(starts_with("event_hosp_")) == 1, na.rm = TRUE), 1, 0),
    time_to_any_hosp = {
      if (any_hosp == 1) {
        events <- c_across(starts_with("event_hosp_"))
        times  <- c_across(starts_with("time_to_event_hosp_"))
        valid  <- which(events == 1 & !is.na(times))
        if (length(valid) > 0) min(times[valid], na.rm = TRUE) else NA_real_
      } else {
        NA_real_
      }
    }
  ) %>%
  ungroup() %>% select(record_id, any_hosp, time_to_any_hosp)

# Censor at 90 days
overall_hosp <- overall_hosp %>% mutate(
  any_hosp = case_when(
    any_hosp == 1 & time_to_any_hosp > 90 ~ 0,
    TRUE ~ any_hosp
  ),
  time_to_any_hosp = case_when(
    any_hosp == 1 & time_to_any_hosp > 90 ~ 90,
    any_hosp == 0 ~ 90,
    TRUE ~ time_to_any_hosp
  )
)
```

## 4.5 Create final_master (merge side_effect and drug indicators)

```{r}
#| label: load-create-final-master
# Cohort filtering (excl. missing cystatin C / platinum) happens in section 5.4.
# eGFR and AE outcomes are now computed from RPDR in sections 4.8–4.9.
final_master <- master %>%
  merge(side_effect, by = "record_id", all.x = TRUE) %>%
  merge(overall_hosp, by = "record_id", all.x = TRUE)

final_master <- create_drug_indicators(final_master)
```

## 4.6 Rename date variables; coerce types

```{r}
#| label: load-rename-dates
# bl_date → baseline_sample_date
# fu_date → last_follow_up_date
final_master <- final_master %>%
  rename(
    baseline_sample_date = bl_date,
    last_follow_up_date  = fu_date
  )

final_master$last_follow_up_date  <- as.Date(final_master$last_follow_up_date)
final_master$baseline_sample_date <- as.Date(final_master$baseline_sample_date)
final_master$platin_dose          <- as.numeric(final_master$platin_dose)
```

## 4.7 Load RPDR files

```{r}
#| label: load-rpdr


# Diagnoses
dia <- read.table('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/Thoracic Oncology Spreadsheets/Carboplatin Paper/RPDR 2026-03-19/mes98_03182614492143216_Dia.txt',
  sep = "|", fill = TRUE, quote = "", header = TRUE)
dia$Date <- as.Date(dia$Date, "%m/%d/%Y")

# Labs (HGB, PLT, ALB, CRE, K, MG, NA — single pull)
lab <- read.table('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/Thoracic Oncology Spreadsheets/Carboplatin Paper/RPDR 2026-03-19/mes98_03182614492143216_Lab.txt',
  sep = "|", fill = TRUE, quote = "", header = TRUE) %>%
  select(EMPI, Seq_Date_Time, Result, Group_Id, Test_Description)
lab$Seq_Date_Time <- as.Date(lab$Seq_Date_Time, "%m/%d/%Y")

# Medications
med <- read.table('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/Thoracic Oncology Spreadsheets/Carboplatin Paper/RPDR 2026-03-19/mes98_03182614492143216_Med.txt',
  sep = "|", fill = TRUE, quote = "", header = TRUE) %>%
  select(EMPI, Medication_Date, Medication)
med$Medication_Date <- as.Date(med$Medication_Date, "%m/%d/%Y")

# Patient index: EMPI + baseline date (needed by pre/post lab functions)
master_list <- final_master %>% select(EMPI, baseline_sample_date)

master_lab     <- merge(master_list, lab,     by = "EMPI", all.x = TRUE)
master_dia     <- merge(master_list, dia,     by = "EMPI", all.y = TRUE)
master_med     <- merge(master_list, med,     by = "EMPI", all.y = TRUE)

# Exclude patients with no RPDR labs
empis_with_labs <- unique(lab$EMPI[lab$EMPI %in% final_master$EMPI])
empis_no_labs   <- setdiff(final_master$EMPI, empis_with_labs)
n_no_labs       <- length(empis_no_labs)

cat("Patients before RPDR lab exclusion:", nrow(final_master), "\n")
cat("Patients with no RPDR labs (excluded):", n_no_labs, "\n")
if (n_no_labs > 0) {
  cat("  record_ids:",
      paste(final_master$record_id[final_master$EMPI %in% empis_no_labs], collapse = ", "), "\n")
}

final_master <- final_master %>% filter(EMPI %in% empis_with_labs)
master_lab   <- master_lab %>% filter(EMPI %in% empis_with_labs)

cat("Patients after RPDR lab exclusion:", nrow(final_master), "\n")
```

## 4.8 Pipeline functions: eGFR formulas

**Variables produced by this pipeline:**

| In Code | Formula | Description |
|---|---|---|
| `male` | `sex == "Male"` | 0/1, required by CKD-EPI |
| `BSA` | DuBois | Body surface area (m²) |
| `baseline_cre_egfr` | CKD-EPI 2012 Cr | Indexed creatinine eGFR |
| `baseline_cys_c_egfr` | CKD-EPI 2012 CysC | Indexed cystatin eGFR |
| `ckd_epi_gfr_cre_cys_unindex` | CKD-EPI 2012 combined, unindexed | Primary combined eGFR for exposures |
| `baseline_cre_egfr_unindexed` | Cr eGFR × BSA/1.73 | Body-adjusted |
| `baseline_cys_c_egfr_unindexed` | CysC eGFR × BSA/1.73 | Body-adjusted |
| `pre_CRE_45days` | `pre_lab()` | Baseline CRE for AKI grading |
| `post_Anemia_2/3_cutpoint_90days` | `post_lab_less_than_cutpoint()` | Grade 2/3 anemia (HGB) |
| `post_Throm_2/3_cutpoint_90days` | `post_lab_less_than_cutpoint()` | Grade 2/3 thrombocytopenia (PLT) |
| `post_AKI_2/3_cutpoint_90days` | CRE > 1.5×/3× pre-baseline CRE | Grade 2/3 AKI (CTCAE) |


```{r}
#| label: fn-pipeline-ckd-epi-cre
# CKD-EPI 2012 creatinine-based eGFR (race-free CKD-EPI equation)
ckd_epi_gfr <- function(cre, male, age) {
  k <- ifelse(male == 1, 0.9, 0.7)
  a <- ifelse(male == 1, -0.302, -0.241)
  m <- ifelse(male == 1, 1, 1.012)
  gfr <- 142 * min(c(cre/k, 1))^a * max(c(cre/k, 1))^-1.2 * 0.9938^age * m
  return(gfr)
}
```

```{r}
#| label: fn-pipeline-ckd-epi-cys
# CKD-EPI 2012 cystatin C-based eGFR (Inker et al. 2012)
# Age coefficient = 0.996 per official NKF/Inker 2012 (not 0.9961, which is the 2021 Cr+CysC value)
ckd_epi_cys_gfr <- function(cys, male, age) {
  gfr <- 133 * min(c(cys/0.8, 1))^(-0.499) * max(c(cys/0.8, 1))^(-1.328) *
         0.996^age * ifelse(male == 0, 0.932, 1)
  return(gfr)
}
```

```{r}
#| label: fn-pipeline-ckd-epi-cre-cys
# Combined creatinine + cystatin C eGFR — exact coefficients from R code summary.Rmd
# Note: coefficients differ from CKD-EPI 2021 race-free (a=-0.144/-0.219, max_cr=-0.544,
# min_cys=-0.323, max_cys=-0.778, age=0.9961, female=0.963)
ckd_epi_cre_cys_gfr <- function(creatinine, cystatin_c, male, age) {
  k      <- ifelse(male == 1, 0.9, 0.7)
  a      <- ifelse(male == 1, -0.144, -0.219)
  female <- ifelse(male == 0, 0.963, 1)
  gfr_cr_cys <- 135 *
    min(c(creatinine/k, 1.0))^a  *
    max(c(creatinine/k, 1.0))^(-0.544) *
    min(c(cystatin_c/0.8, 1.0))^(-0.323) *
    max(c(cystatin_c/0.8, 1.0))^(-0.778) *
    0.9961^age * female
  return(gfr_cr_cys)
}
```

```{r}
#| label: fn-pipeline-cockcroft
# Cockcroft-Gault creatinine clearance (mL/min)
# Female factor = 0.85; male = 1.0
Cockcroft <- function(age, weight, male, cre) {
  if (male == 0) {
    value <- (140 - age) * weight * 0.85 / (72 * cre)
  } else {
    value <- (140 - age) * weight / (72 * cre)
  }
  return(value)
}
```

```{r}
#| label: fn-pipeline-unindex
# Adjust indexed eGFR for body surface area
unindex <- function(value, bsa) {
  return(value * bsa / 1.73)
}
```

## 4.9 Pipeline execution: pre-labs, eGFR, AE outcomes

```{r}
#| label: pipeline-derived-vars
# male (0/1) and BSA are required by all eGFR formulas
final_master <- final_master %>%
  mutate(
    male = case_when(
      sex %in% c("Male", "male", 1)    ~ 1,
      sex %in% c("Female", "female", 2) ~ 0,
      TRUE ~ NA_real_
    ),
    BSA = 0.007184 * (weight ^ 0.425) * (height ^ 0.725)
  )
```

```{r}
#| label: pipeline-pre-labs
# pre_CRE_45days: baseline creatinine (AKI grade 2/3 reference denominator)
pre_CRE_45days <- pre_lab(master_lab, month = FALSE, time = 45,
                           index_date = baseline_sample_date, Group_Id = "CRE")

# Haematology / biochemistry pre-baseline labs
pre_HGB_45days <- pre_lab(master_lab, month = FALSE, time = 45,
                           index_date = baseline_sample_date, Group_Id = "HGB")
pre_PLT_45days <- pre_lab(master_lab, month = FALSE, time = 45,
                           index_date = baseline_sample_date, Group_Id = "PLT")
pre_ALB_45days <- pre_lab(master_lab, month = FALSE, time = 45,
                           index_date = baseline_sample_date, Group_Id = "ALB")
pre_GHBA1C_45days <- pre_lab(master_lab, month = FALSE, time = 45,
                              index_date = baseline_sample_date, Group_Id = "GHBA1C")

# Merge all pre-baseline labs into final_master
final_master <- final_master %>%
  merge(pre_CRE_45days,    by = "EMPI", all.x = TRUE) %>%
  merge(pre_HGB_45days,    by = "EMPI", all.x = TRUE) %>%
  merge(pre_PLT_45days,    by = "EMPI", all.x = TRUE) %>%
  merge(pre_ALB_45days,    by = "EMPI", all.x = TRUE) %>%
  merge(pre_GHBA1C_45days, by = "EMPI", all.x = TRUE)
```

```{r}
#| label: pipeline-egfr
# All eGFR variables computed via mapply() (scalar functions over rows).
# Uses PDF names baseline_creatinine and cys_c_baseline (renamed in section 5.8).
final_master <- final_master %>%
  mutate(
    cys_c_baseline      = as.numeric(cys_c_baseline),
    baseline_creatinine = as.numeric(baseline_creatinine),
  ) %>%
  mutate(
    baseline_cre_egfr            = mapply(ckd_epi_gfr, baseline_creatinine, male, age),
    baseline_cys_c_egfr          = mapply(ckd_epi_cys_gfr, cys_c_baseline, male, age),
    ckd_epi_gfr_cre_cys          = mapply(ckd_epi_cre_cys_gfr,
                                          baseline_creatinine, cys_c_baseline, male, age),
    baseline_cre_egfr_unindexed  = mapply(unindex, baseline_cre_egfr, BSA),
    baseline_cys_c_egfr_unindexed = mapply(unindex, baseline_cys_c_egfr, BSA),
    ckd_epi_gfr_cre_cys_unindex  = mapply(unindex, ckd_epi_gfr_cre_cys, BSA),
    ckd_epi_gfr_cre_cys_unindex_cap125 = pmin(ckd_epi_gfr_cre_cys_unindex, 125),
    cockcroft                          = mapply(Cockcroft, age, weight, male, baseline_creatinine)
  )
```

```{r}
#| label: pipeline-ae-labs
# Post-baseline AE lab outcomes (from RPDR lab — original pull).
# Dates are already Date type from section 4.7; no further conversion needed.

Anemia_g2_value <- post_lab_less_than_cutpoint(
  data = master_lab, days = 90, index_date = baseline_sample_date,
  Group_ID = "HGB", Group_ID_name = "Anemia_2", cutpoint = 10)   # HGB < 10 g/dL

Anemia_g3_value <- post_lab_less_than_cutpoint(
  data = master_lab, days = 90, index_date = baseline_sample_date,
  Group_ID = "HGB", Group_ID_name = "Anemia_3", cutpoint = 8)    # HGB < 8 g/dL

Throm_g2_value <- post_lab_less_than_cutpoint(
  data = master_lab, days = 90, index_date = baseline_sample_date,
  Group_ID = "PLT", Group_ID_name = "Throm_2", cutpoint = 75)    # PLT < 75×10^9/L

Throm_g3_value <- post_lab_less_than_cutpoint(
  data = master_lab, days = 90, index_date = baseline_sample_date,
  Group_ID = "PLT", Group_ID_name = "Throm_3", cutpoint = 50)    # PLT < 50×10^9/L

# AKI grade 2: post-baseline CRE > 1.5 × pre-baseline CRE (CTCAE)
AKI_g2_value <- master_lab %>%
  merge(pre_CRE_45days, by = "EMPI", all.x = TRUE) %>%
  filter(Group_Id == "CRE") %>%
  filter(grepl("^[><]?\\d+\\.?\\d* ?$", Result)) %>%
  mutate(Result = as.numeric(parse_number(Result))) %>%
  filter(!is.na(Result), !is.na(pre_CRE_45days)) %>%
  filter(Seq_Date_Time > baseline_sample_date,
         Seq_Date_Time <= baseline_sample_date + 90) %>%
  filter(Result > 1.5 * pre_CRE_45days) %>%
  arrange(EMPI, Seq_Date_Time) %>%
  distinct(EMPI, .keep_all = TRUE) %>%
  select(EMPI, Result, Seq_Date_Time) %>%
  rename(post_AKI_2_cutpoint_90days      = Result,
         post_AKI_2_cutpoint_90days_date = Seq_Date_Time)

# AKI (KDIGO): Rule 1 — CRE >= 1.5 × pre-baseline CRE
#              Rule 2 — any 2-day window with CRE increase >= 0.3 mg/dL
# Either rule triggers AKI; first qualifying date is used.
aki_kdigo_cre <- master_lab %>%
  merge(pre_CRE_45days, by = "EMPI", all.x = TRUE) %>%
  filter(Group_Id == "CRE") %>%
  filter(grepl("^[><]?\\d+\\.?\\d* ?$", Result)) %>%
  mutate(Result = as.numeric(parse_number(Result))) %>%
  filter(!is.na(Result), !is.na(pre_CRE_45days)) %>%
  filter(Seq_Date_Time > baseline_sample_date,
         Seq_Date_Time <= baseline_sample_date + 90) %>%
  arrange(EMPI, Seq_Date_Time)

# Rule 1: CRE >= 1.5 × pre-baseline
aki_rule1 <- aki_kdigo_cre %>%
  filter(Result >= 1.5 * pre_CRE_45days) %>%
  distinct(EMPI, .keep_all = TRUE) %>%
  select(EMPI, aki_date_r1 = Seq_Date_Time, aki_value_r1 = Result)

# Rule 2: within any 2-day window, CRE increased by >= 0.3 from lowest CRE in prior 2 days
aki_rule2 <- aki_kdigo_cre %>%
  group_by(EMPI) %>%
  mutate(
    lowest_cre_2d = purrr::map_dbl(seq_along(Seq_Date_Time), function(i) {
      window <- Result[Seq_Date_Time >= (Seq_Date_Time[i] - 2) &
                       Seq_Date_Time < Seq_Date_Time[i]]
      if (length(window) == 0) NA_real_ else min(window, na.rm = TRUE)
    })
  ) %>%
  ungroup() %>%
  filter(!is.na(lowest_cre_2d), Result >= lowest_cre_2d + 0.3) %>%
  arrange(EMPI, Seq_Date_Time) %>%
  distinct(EMPI, .keep_all = TRUE) %>%
  select(EMPI, aki_date_r2 = Seq_Date_Time, aki_value_r2 = Result)

# Combine: earliest date from either rule
AKI_kdigo_value <- merge(aki_rule1, aki_rule2, by = "EMPI", all = TRUE) %>%
  mutate(
    post_AKI_kdigo_cutpoint_90days_date = pmin(aki_date_r1, aki_date_r2, na.rm = TRUE),
    post_AKI_kdigo_cutpoint_90days = case_when(
      is.na(aki_date_r2) ~ aki_value_r1,
      is.na(aki_date_r1) ~ aki_value_r2,
      aki_date_r1 <= aki_date_r2 ~ aki_value_r1,
      TRUE ~ aki_value_r2
    )
  ) %>%
  select(EMPI, post_AKI_kdigo_cutpoint_90days, post_AKI_kdigo_cutpoint_90days_date)

# AKI grade 3: post-baseline CRE > 3 × pre-baseline CRE (CTCAE)
AKI_g3_value <- master_lab %>%
  merge(pre_CRE_45days, by = "EMPI", all.x = TRUE) %>%
  filter(Group_Id == "CRE") %>%
  filter(grepl("^[><]?\\d+\\.?\\d* ?$", Result)) %>%
  mutate(Result = as.numeric(parse_number(Result))) %>%
  filter(!is.na(Result), !is.na(pre_CRE_45days)) %>%
  filter(Seq_Date_Time > baseline_sample_date,
         Seq_Date_Time <= baseline_sample_date + 90) %>%
  filter(Result > 3 * pre_CRE_45days) %>%
  arrange(EMPI, Seq_Date_Time) %>%
  distinct(EMPI, .keep_all = TRUE) %>%
  select(EMPI, Result, Seq_Date_Time) %>%
  rename(post_AKI_3_cutpoint_90days      = Result,
         post_AKI_3_cutpoint_90days_date = Seq_Date_Time)

# Merge AE outcomes into final_master
final_master <- final_master %>%
  merge(Anemia_g2_value, by = "EMPI", all.x = TRUE) %>%
  merge(Anemia_g3_value, by = "EMPI", all.x = TRUE) %>%
  merge(Throm_g2_value,  by = "EMPI", all.x = TRUE) %>%
  merge(Throm_g3_value,  by = "EMPI", all.x = TRUE) %>%
  merge(AKI_g2_value,    by = "EMPI", all.x = TRUE) %>%
  merge(AKI_g3_value,    by = "EMPI", all.x = TRUE) %>%
  merge(AKI_kdigo_value, by = "EMPI", all.x = TRUE)
```

---

# 5 Data Cleaning & Variable Creation

## 5.1 Mortality variables

```{r}
#| label: clean-mortality
# days_last_follow_up: numeric days from baseline to last known follow-up date
final_master <- final_master %>%
  mutate(days_last_follow_up = as.numeric(last_follow_up_date - baseline_sample_date))

# decode pt_status (PDF name kept) to character label
final_master <- final_master %>%
  mutate(pt_status = case_when(
    pt_status == 1 ~ "Alive",
    pt_status == 2 ~ "On Hospice",
    pt_status == 3 ~ "Dead"
  ))

# time_to_death_90: follow-up time capped at 90 days
# time_to_death_90_status: 0=alive/censored, 2=dead (competing-risk coding)
# death_90: binary 0/1
final_master <- final_master %>%
  mutate(
    time_to_death_90 = ifelse(days_last_follow_up > 90, 90, days_last_follow_up),
    time_to_death_90_status = case_when(
      days_last_follow_up > 90                          ~ 0,
      days_last_follow_up <= 90 & pt_status == "Dead"  ~ 2,
      days_last_follow_up <= 90 & pt_status != "Dead"  ~ 0
    ),
    death_90    = ifelse(time_to_death_90_status == 2, 1, 0)
  )
```

## 5.2 Censor hospitalization time variables at 90 days

```{r}
#| label: clean-hosp-censor
# For each reason 1–11: no-event patients get time = 90 (censored)
for (i in 1:11) {
  event_col <- paste0("event_hosp_", i)
  time_col  <- paste0("time_to_event_hosp_", i)
  final_master[[time_col]][final_master[[event_col]] == 0] <- 90
}
```

## 5.3 Adverse event outcome variables (from RPDR pipeline)

```{r}
#| label: clean-ae-outcomes
# AE dates come from RPDR (Seq_Date_Time), already Date type — no conversion needed.

# Binary AE flags: 1 if cutpoint value is non-missing (event occurred within 90 days)
final_master <- final_master %>%
  mutate(
    Anemia_g2_90days = ifelse(!is.na(post_Anemia_2_cutpoint_90days), 1, 0),
    Anemia_g3_90days = ifelse(!is.na(post_Anemia_3_cutpoint_90days), 1, 0),
    Throm_g2_90days  = ifelse(!is.na(post_Throm_2_cutpoint_90days),  1, 0),
    Throm_g3_90days  = ifelse(!is.na(post_Throm_3_cutpoint_90days),  1, 0),
    AKI_g2_90days    = ifelse(!is.na(post_AKI_2_cutpoint_90days),    1, 0),
    AKI_g3_90days    = ifelse(!is.na(post_AKI_3_cutpoint_90days),    1, 0),
    AKI_kdigo_90days = ifelse(!is.na(post_AKI_kdigo_cutpoint_90days), 1, 0)
  )

# Time-to-AE in days; NA (no event) replaced with 90 (censored)
final_master <- final_master %>%
  mutate(
    time_to_anemia_2 = post_Anemia_2_cutpoint_90days_date - baseline_sample_date,
    time_to_anemia_3 = post_Anemia_3_cutpoint_90days_date - baseline_sample_date,
    time_to_throm_2  = post_Throm_2_cutpoint_90days_date  - baseline_sample_date,
    time_to_throm_3  = post_Throm_3_cutpoint_90days_date  - baseline_sample_date,
    time_to_aki_2    = post_AKI_2_cutpoint_90days_date    - baseline_sample_date,
    time_to_aki_3    = post_AKI_3_cutpoint_90days_date    - baseline_sample_date,
    time_to_aki_kdigo = post_AKI_kdigo_cutpoint_90days_date - baseline_sample_date
  ) %>%
  mutate(across(
    c(time_to_anemia_2, time_to_anemia_3,
      time_to_throm_2,  time_to_throm_3,
      time_to_aki_2,    time_to_aki_3,
      time_to_aki_kdigo),
    ~ ifelse(is.na(.), 90, as.numeric(.))   # no-event patients censored at 90 days
  ))

# grade_2_aes: composite — any of anemia / throm / AKI grade 2
# grade_3_aes: composite — any of anemia / throm / AKI grade 3
final_master <- final_master %>%
  mutate(
    grade_2_aes = case_when(
      Anemia_g2_90days == 1 | Throm_g2_90days == 1 | AKI_g2_90days == 1 ~ 1,
      TRUE ~ 0
    ),
    grade_3_aes = case_when(
      Anemia_g3_90days == 1 | Throm_g3_90days == 1 | AKI_g3_90days == 1 ~ 1,
      TRUE ~ 0
    )
  )
```

## 5.4 Exclusion filter: missing cystatin C or platinum type

```{r}
#| label: clean-exclusion
# Exclude patients missing baseline cystatin C or platinum group
final_master <- final_master %>%
  mutate(cys_c_baseline = as.numeric(cys_c_baseline))

cat("Missing cystatin C — record_id:",
    paste(final_master$record_id[is.na(final_master$cys_c_baseline)], collapse = ", "), "\n")
cat("Missing platinum group — record_id:",
    paste(final_master$record_id[is.na(final_master$platin_group)], collapse = ", "), "\n")

final_master <- final_master %>%
  filter(!is.na(cys_c_baseline)) %>%
  filter(!is.na(platin_group))
```

## 5.5 Exposure variables

```{r}
#| label: clean-exposure
# cr_cys: raw ratio (creatinine / cystatin C)
final_master$cr_cys <- final_master$baseline_creatinine / final_master$cys_c_baseline

# cr_cys_cat: four ordered categories
final_master <- final_master %>%
  mutate(cr_cys_cat = case_when(
    cr_cys < 0.5                  ~ 1,
    cr_cys >= 0.5 & cr_cys < 0.7 ~ 2,
    cr_cys >= 0.7 & cr_cys < 0.9 ~ 3,
    cr_cys >= 0.9                 ~ 4
  ))
final_master$cr_cys_cat <- factor(
  final_master$cr_cys_cat,
  levels = c("1", "2", "3", "4"),
  labels = c("< 0.5", "0.5-0.7", "0.7-0.9", "≥ 0.9")
)

# cr_cys_7: primary binary exposure — 1 if cr_cys < 0.7
final_master$cr_cys_7 <- ifelse(final_master$cr_cys < 0.7, 1, 0)

# Alternative eGFR-based exposure
final_master <- final_master %>%
  mutate(
    # 30% discrepancy: cystatin eGFR vs creatinine eGFR (CKD-EPI)
    exposure_epi_30 = ifelse(baseline_cys_c_egfr < 0.7 * baseline_cre_egfr, 1, 0)
  )

table(final_master$cr_cys_7)
```

## 5.6 BMI, age categories, ICI, CKD stage

```{r}
#| label: clean-categories
# bmi: calculated from height (cm) and weight (kg)
# bmi_cat: 1=underweight <18.5, 2=normal 18.5–25, 3=overweight 25–30, 4=obese ≥30
# age_cat: 1=≤65, 2=66–80, 3=>80
# ici: immunotherapy co-administration (Atezolizumab OR Pembrolizumab OR Durvalumab)
final_master <- final_master %>%
  mutate(
    bmi = weight / (height / 100)^2,
    bmi_cat = factor(case_when(
      bmi < 18.5              ~ "Underweight (<18.5)",
      bmi >= 18.5 & bmi < 25 ~ "Normal (18.5-25)",
      bmi >= 25   & bmi < 30 ~ "Overweight (25-30)",
      bmi >= 30               ~ "Obese (>=30)",
      TRUE ~ NA_character_
    ), levels = c("Underweight (<18.5)", "Normal (18.5-25)", "Overweight (25-30)", "Obese (>=30)")),
    age_cat = factor(case_when(
      age <= 65             ~ "<=65",
      age > 65 & age <= 80 ~ "66-80",
      age > 80              ~ ">80"
    ), levels = c("<=65", "66-80", ">80")),
    ici = ifelse(Atezolizumab == 1 | Pembrolizumab == 1 | Durvalumab == 1, 1, 0)
  )
```

## 5.7 Label REDCap coded variables

```{r}
#| label: clean-labels
# Apply human-readable labels to REDCap numeric-coded variables (per data dictionary)
final_master <- final_master %>%
  mutate(
    sex        = factor(sex, levels = c(2, 1), labels = c("Female", "Male")),
    race       = factor(race, levels = 1:5, labels = c("White", "Black", "Asian", "Other", "Unknown")),
    ethnicity  = factor(ethnicity, levels = 1:3, labels = c("Non-Hispanic", "Hispanic", "Unknown")),
    tumor_stage = factor(tumor_stage, levels = c(1, 2), labels = c("Local/Early", "Advanced/Metastatic")),
    platin_group = factor(platin_group, levels = 1:3, labels = c("Carboplatin", "Cisplatin", "Unknown")),
    # ecog_score: REDCap codes 1=ECOG 0, 2=ECOG 1, ..., 7=N/A
    ecog_score = case_when(
      ecog_score >= 1 & ecog_score <= 6 ~ ecog_score - 1,  # remap to actual ECOG 0–5
      ecog_score == 7 ~ NA_real_,                           # N/A → missing
      TRUE ~ NA_real_
    ),
    ecog_estimate = case_when(
      ecog_estimate >= 1 & ecog_estimate <= 6 ~ ecog_estimate - 1,
      TRUE ~ NA_real_
    )
  ) %>%
  droplevels()
```

## 5.8 Cancer type categories (7 groups)

```{r}
#| label: clean-cancer-type-cat
# cancer_type_cat_7: recode REDCap tumor_type (numeric 1–9) into 7 clinical groups
# REDCap coding (from data dictionary):
#   1 = Lung → Thoracic
#   2 = Breast
#   3 = Upper GI/esophagus/gastric  → GI
#   4 = Lower GI/colon/rectum      → GI
#   5 = Genitourinary/RCC/bladder   → GU
#   6 = Mesothelioma                → Other
#   7 = Gyn/ovarian/uterus/cervix  → GYN
#   8 = HEENT/Laryngeal/head & neck → HEENT
#   9 = Other                       → Other
final_master <- final_master %>%
  mutate(
    cancer_type_cat_7 = factor(case_when(
      tumor_type == 1             ~ 1,   # Thoracic (Lung)
      tumor_type == 2             ~ 2,   # Breast
      tumor_type %in% c(3, 4)    ~ 3,   # GI (Upper + Lower)
      tumor_type == 5             ~ 4,   # GU
      tumor_type == 7             ~ 5,   # GYN
      tumor_type == 8             ~ 6,   # HEENT
      tumor_type %in% c(6, 9)    ~ 7,   # Other (Mesothelioma + Other)
      TRUE ~ NA_real_
    ), levels = 1:7, labels = c("Thoracic", "Breast", "GI", "GU", "GYN", "HEENT", "Other"))
  )

table(final_master$cancer_type_cat_7)
```

## 5.8 Platinum dosing variables

```{r}
#| label: clean-platinum
# carbo / cis: binary platinum type (platin_group is now a labeled factor)
# carbo_AUC: carboplatin AUC (from platin_dose); cis_dose: cisplatin mg/m²
# cis_group: cisplatin dose tier (1=<40, 2=40–60, 3=≥60 mg/m²)
# dose_1: high-dose flag (carbo AUC≥5 OR cisplatin≥75 mg/m²)
# carbo_AUC_cat: "<3" vs ">=3" (factor, NA if not carboplatin)
# cis_dose_cat: 1=<75 mg/m², 2=≥75, 0=not cisplatin
final_master <- final_master %>%
  mutate(
    carbo        = ifelse(platin_group == "Carboplatin", 1, 0),
    cis          = ifelse(platin_group == "Cisplatin",   1, 0),
    carbo_AUC    = case_when(carbo == 1 ~ platin_dose, TRUE ~ NA_real_),
    cis_dose     = case_when(cis == 1 ~ platin_dose, TRUE ~ NA_real_),
    cis_group    = case_when(
      cis_dose < 40                    ~ 1,
      cis_dose >= 40 & cis_dose < 60  ~ 2,
      cis_dose >= 60                   ~ 3,
      TRUE ~ NA_real_
    ),
    high_dose = factor(case_when(
      carbo_AUC >= 5 | cis_dose >= 75 ~ 1,
      carbo_AUC <  5 | cis_dose <  75 ~ 0,
      TRUE ~ NA_real_
    )),
    carbo_AUC_cat = factor(case_when(
      carbo_AUC < 3  ~ "<3",
      carbo_AUC >= 3 ~ ">=3",
      TRUE ~ NA_character_
    ), levels = c("<3", ">=3")),
    cis_dose_cat = case_when(
      cis_dose <  75 ~ 1,
      cis_dose >= 75 ~ 2,
      TRUE ~ 0
    ),
    # Labeled cisplatin dose factor for Table 1 (NA for non-cisplatin patients,
    # symmetric to carbo_AUC_cat which is NA for non-carboplatin patients)
    cis_dose_high = factor(case_when(
      cis_dose <  75 ~ "<75",
      cis_dose >= 75 ~ ">=75",
      TRUE ~ NA_character_
    ), levels = c("<75", ">=75"))
  )

table(final_master$high_dose)
```

## 5.9 Carboplatin dose discrepancy variables (from Leyre dose.Rmd)

```{r}
#| label: clean-dose-carbo
# Carboplatin is dosed via Calvert formula: Dose(mg) = target AUC × (GFR + 25)
# The actual administered dose is recorded in REDCap (dosage_mg).
# CKD-EPI Cr-Cys eGFR predicts what the dose should be — the discrepancy
# between actual and predicted may relate to adverse outcomes.
#
# carbo_dose_redcap:  actual administered dose from REDCap (dosage_mg)
# carbo_dose_cre_cys: predicted dose using CKD-EPI Cr-Cys unindexed eGFR
# dose_discrepancy:   actual - predicted (mg); positive = patient got more than CKD-EPI predicts
# dose_diff_pct:      (actual - predicted) / predicted × 100

final_master <- final_master %>%
  mutate(
    carbo_dose_redcap  = as.numeric(dosage_mg),
    carbo_dose_cre_cys = carbo_AUC * (ckd_epi_gfr_cre_cys_unindex_cap125 + 25),
    dose_discrepancy   = carbo_dose_redcap - carbo_dose_cre_cys,
    dose_diff_pct      = (carbo_dose_redcap - carbo_dose_cre_cys) / carbo_dose_cre_cys * 100,
    dd_gt25            = factor(ifelse(!is.na(dose_discrepancy) & dose_discrepancy > 25, 1, 0)),
    dd_gt50            = factor(ifelse(!is.na(dose_discrepancy) & dose_discrepancy > 50, 1, 0)),
    ecog_score_cat2    = factor(ifelse(ecog_score == 0, "0", ">=1"), levels = c("0", ">=1")),
    bmi_30 = factor(ifelse(bmi < 30, "<30", ">=30")),
    age_70 = factor(ifelse(age < 70, "<70", ">=70"))
  )
```

## 5.10 Rename baseline lab variables (Copy 709 convention)

```{r}
#| label: clean-rename-labs
# baseline_cre: from baseline_creatinine (PDF name)
# baseline_cre: from baseline_creatinine (PDF name)
# baseline_cys_c: from cys_c_baseline (PDF name)
final_master <- final_master %>%
  rename(
    baseline_cre   = baseline_creatinine,
    baseline_cys_c = cys_c_baseline
  )
```

## 5.10 Electrolyte outcomes — removed

> K, MG, NA not in current RPDR lab pull (only ALB, CRE, HGB, PLT, GHBA1C).
> Hypokalemia, Hypomagnesemia, Hyponatremia outcomes removed.

## 5.11 Thyroid disease (RPDR diagnosis + medication)

```{r}
#| label: clean-thyroid
thyroid <- c("hypothyroidism", "hyperthyroidism", "thyroiditis")
thyroid_med_list <- c("Methimazole", "Tapazole", "Propylthiouracil", "Potassium Iodide",
                      "Radioactive Iodine ", "levothyroxine", "Euthyrox", "Synthroid",
                      "Eltroxin", "Desiccated Thyroid Extract", "Armour Thyroid")

thyroid_final <- dia_list_name(
  master_dia,
  listed_names = thyroid,
  med_data     = master_med,
  med_names    = thyroid_med_list,
  index_date   = baseline_sample_date
)

# thyroid: 1 if diagnosed or treated for thyroid disease before baseline
final_master <- final_master %>%
  mutate(thyroid = ifelse(EMPI %in% thyroid_final$EMPI, 1, 0))
```

## 5.12 Smoking status (RPDR diagnosis)

```{r}
#| label: clean-smoking
# smoking: 1 if tobacco/smoking-related diagnosis found before baseline
smoking_terms <- c(
  "tobacco use", "tobacco dependence", "tobacco abuse",
  "nicotine dependence", "nicotine use",
  "smoking", "smoker", "cigarette"
)

smoking_final <- dia_list_name(
  master_dia,
  listed_names = smoking_terms,
  index_date   = baseline_sample_date
)

final_master <- final_master %>%
  mutate(smoking = ifelse(EMPI %in% smoking_final$EMPI, 1, 0))
```

## 5.13 Corticosteroid use (RPDR medication)

```{r}
#| label: clean-steroids
# steroids: 1 if corticosteroid medication dispensed within 30 days before baseline.
# The exclusion list (no_steroid_names) follows the reference definition in
# "Reference code/prospective cys.Rmd": drop inhaled, nebulized, topical,
# ophthalmic, and Symbicort dispensings so the flag reflects systemic
# corticosteroid use, not puffers / creams / eye drops.
steroid_med_list <- c(
  "Prednisone", "Prednisolone", "Methylprednisolone", "Medrol",
  "Dexamethasone", "Decadron", "Hydrocortisone", "Cortisol",
  "Budesonide", "Triamcinolone", "Betamethasone", "Fludrocortisone",
  "Cortisone"
)
no_steroid_names <- c("Inhaler", "Nebulization", "Ointment", "Ophthalmic", "Symbicort")

steroid_final <- master_med %>%
  filter(!is.na(Medication_Date),
         Medication_Date <= baseline_sample_date,
         Medication_Date >= baseline_sample_date - 30) %>%
  filter(grepl(paste(steroid_med_list, collapse = "|"), Medication, ignore.case = TRUE),
         !grepl(paste(no_steroid_names, collapse = "|"), Medication, ignore.case = TRUE)) %>%
  distinct(EMPI)

final_master <- final_master %>%
  mutate(steroids = ifelse(EMPI %in% steroid_final$EMPI, 1, 0))
```

## 5.14 HIV from RPDR (hiv_rpdr)

```{r}
#| label: clean-hiv-rpdr
# hiv_rpdr: HIV status from RPDR diagnoses + medications (Jiaxuan's pipeline).
# Note: There is no hiv column in the REDCap CSV. The hiv variable in Copy 709 / cleaned_master
# was always derived from RPDR. Jiaxuan's final code Rmd used the name hiv_new.
#
# Step 1: dia_list_name with HIV terms, excluding false-positive diagnosis names
# Step 2: Further exclude patients whose HIV diagnosis co-occurs with hepatitis B/C

no_hiv <- c(
  "1 - Hives-Oncall",
  "Contact with and (suspected) exposure to human immunodeficiency virus [hiv]",
  "Encounter for screening for human immunodeficiency virus [hiv]",
  "counseling",
  "Inconclusive laboratory evidence of human immunodeficiency virus [hiv]",
  "Asymptomatic human immunodeficiency virus [hiv] infection status",
  "Family history of human immunodeficiency virus [hiv] disease",
  "HIV exposure-Oncall"
)

hiv_terms <- c("hiv", "human immunodeficiency virus")

hiv_med_list <- c(
  "abacavir", "ziagen", "emtricitabine", "emtriva", "lamivudine", "tenofovir", "viread",
  "zidovudine", "retrovir", "doravirine", "pifeltro", "efavirenz", "sustiva", "etravirine",
  "intelence", "nevirapine", "viramune", "rilpivirine", "edurant", "atazanavir", "reyataz",
  "darunavir", "prezista", "fosamprenavir", "lexiva", "ritonavir", "norvir", "saquinavir",
  "invirase", "tipranavir", "aptivus", "enfuvirtide", "fuzeon", "maraviroc", "selzentry",
  "cabotegravir", "vocabria", "dolutegravir", "tivicay", "raltegravir", "isentress", "fostemsavir",
  "rukobia", "ibalizumab", "trogarzo", "lenacapavir", "sunlenca",
  "atripla", "biktarvy", "cabenuva", "cimduo", "combivir", "complera", "descovy", "dovato",
  "epzicom", "evotaz", "genvoya", "juluca", "kaletra", "odefsey", "prezcobix", "stribild",
  "symtuza", "triumeq", "truvada", "trizivir",
  "didanosine", "stavudine", "videx", "zerit", "delavirdine", "rescriptor", "indinavir",
  "crixivan", "nelfinavir", "viracept", "fortovase"
)

hiv_rpdr_initial <- dia_list_name(
  master_dia,
  listed_names  = hiv_terms,
  excluded_names = no_hiv,
  med_data       = master_med,
  med_names      = hiv_med_list,
  index_date     = baseline_sample_date
)

# Step 2: Further filter — exclude patients whose HIV diagnosis also mentions hepatitis B/C
hiv_rpdr_cleaned <- hiv_rpdr_initial %>%
  left_join(master_dia %>% select(EMPI, Diagnosis_Name), by = "EMPI") %>%
  filter(
    str_detect(Diagnosis_Name, regex("hiv|human immunodeficiency virus", ignore_case = TRUE)),
    !str_detect(Diagnosis_Name, regex("hepatitis B|hepatitis C", ignore_case = TRUE))
  ) %>%
  distinct(EMPI)

final_master <- final_master %>%
  mutate(hiv_rpdr = ifelse(EMPI %in% hiv_rpdr_cleaned$EMPI, 1, 0))

table(final_master$hiv_rpdr)
```


## 5.14 Charlson Comorbidity Index

```{r}
#| label: clean-charlson
### Charlson comorbidity index
ici_diag <- dia %>% subset(select = c(EMPI, Diagnosis_Name, Date, Code, Code_Type))
ici_diag <- ici_diag %>% merge(final_master %>% select(EMPI, baseline_sample_date),
                                by = "EMPI", all.y = TRUE)
ici_diag$Date <- as.Date(ici_diag$Date, "%m/%d/%Y")
ici_diag_pre  <- subset(ici_diag, Date < baseline_sample_date)

# Leukemia and lymphoma must be extracted manually (ICD code map includes them under cancer)
leukemia <- ici_diag_pre[grep("leukemia", ici_diag_pre$Diagnosis_Name, ignore.case = TRUE), ]
leukemia <- leukemia[!grepl("lymphoma", leukemia$Diagnosis_Name, ignore.case = TRUE), ]
leukemia <- as.data.frame(table(leukemia$EMPI))
names(leukemia)[names(leukemia) == "Var1"] <- "EMPI"
names(leukemia)[names(leukemia) == "Freq"] <- "leukemia"
leukemia$leukemia[leukemia$leukemia > 0] <- 1

lymphoma <- ici_diag_pre[grep("lymphoma", ici_diag_pre$Diagnosis_Name, ignore.case = TRUE), ]
lymphoma <- lymphoma[!grepl("leukemia", lymphoma$Diagnosis_Name, ignore.case = TRUE), ]
lymphoma <- as.data.frame(table(lymphoma$EMPI))
names(lymphoma)[names(lymphoma) == "Var1"] <- "EMPI"
names(lymphoma)[names(lymphoma) == "Freq"] <- "lymphoma"
lymphoma$lymphoma[lymphoma$lymphoma > 0] <- 1

leuk_lymph <- merge(leukemia, lymphoma, by = "EMPI", all = TRUE)

# Compute comorbidity scores separately for ICD-9 and ICD-10
diag_icd9  <- subset(ici_diag_pre, Code_Type == "ICD9",  select = c("EMPI", "Code"))
diag_icd10 <- subset(ici_diag_pre, Code_Type == "ICD10", select = c("EMPI", "Code"))
diag_icd9  <- diag_icd9[!(diag_icd9$Code == ""), ]
diag_icd10 <- diag_icd10[!(diag_icd10$Code == ""), ]

charlson9  <- comorbidity(x = diag_icd9,  id = "EMPI", code = "Code",
                           map = "charlson_icd9_quan",  assign0 = FALSE)
charlson10 <- comorbidity(x = diag_icd10, id = "EMPI", code = "Code",
                           map = "charlson_icd10_quan", assign0 = FALSE)

charlson <- merge(charlson9, charlson10, by = "EMPI", all = TRUE)
charlson[is.na(charlson)] <- 0

# Take maximum across ICD-9 / ICD-10 for each domain
charlson$ami      <- pmax(charlson$mi.x,       charlson$mi.y)
charlson$chf      <- pmax(charlson$chf.x,      charlson$chf.y)
charlson$pvd      <- pmax(charlson$pvd.x,      charlson$pvd.y)
charlson$cevd     <- pmax(charlson$cevd.x,     charlson$cevd.y)
charlson$dementia <- pmax(charlson$dementia.x,  charlson$dementia.y)
charlson$copd     <- pmax(charlson$cpd.x,      charlson$cpd.y)
charlson$rheumd   <- pmax(charlson$rheumd.x,   charlson$rheumd.y)
charlson$pud      <- pmax(charlson$pud.x,      charlson$pud.y)
charlson$mld      <- pmax(charlson$mld.x,      charlson$mld.y)
charlson$diab     <- pmax(charlson$diab.x,     charlson$diab.y)
charlson$diabwc   <- pmax(charlson$diabwc.x,   charlson$diabwc.y)
charlson$hp       <- pmax(charlson$hp.x,       charlson$hp.y)
charlson$rend     <- pmax(charlson$rend.x,     charlson$rend.y)
charlson$canc     <- pmax(charlson$canc.x,     charlson$canc.y)
charlson$msld     <- pmax(charlson$msld.x,     charlson$msld.y)
charlson$metacanc <- pmax(charlson$metacanc.x, charlson$metacanc.y)
charlson$aids     <- pmax(charlson$aids.x,     charlson$aids.y)

charlson <- charlson %>%
  subset(select = c(EMPI, ami, chf, pvd, cevd, dementia, copd, rheumd, pud, mld,
                    diab, diabwc, hp, rend, canc, msld, metacanc, aids))
charlson$canc <- 1  # all patients have cancer by definition

charlson <- merge(charlson, leuk_lymph, by = "EMPI", all = TRUE)
charlson[is.na(charlson)] <- 0

ages <- final_master %>% subset(select = c(EMPI, age))
charlson <- merge(charlson, ages, by.x = 1, by.y = 1)

# Weighted Charlson score with age adjustment (Quan 2011)
charlson$score <-
  charlson$ami + charlson$chf + charlson$pvd + charlson$cevd +
  charlson$dementia + charlson$copd + charlson$rheumd + charlson$pud +
  ifelse(charlson$mld == 1 & charlson$msld == 0, 1, 0) +
  ifelse(charlson$msld == 1, 3, 0) +
  charlson$diab + charlson$diabwc +
  charlson$hp * 2 + charlson$rend * 2 + charlson$canc * 2 +
  charlson$metacanc * 4 + charlson$aids * 6 +
  charlson$leukemia * 2 + charlson$lymphoma * 2 +
  ifelse(charlson$age >= 50 & charlson$age < 60, 1, 0) +
  ifelse(charlson$age >= 60 & charlson$age < 70, 2, 0) +
  ifelse(charlson$age >= 70 & charlson$age < 80, 3, 0) +
  ifelse(charlson$age >= 80, 4, 0)

# cci: categorical severity
charlson_sc <- charlson %>% subset(select = c(EMPI, score))
charlson_sc$cci <- ifelse(charlson_sc$score < 3, "mild",
                   ifelse(charlson_sc$score >= 3 & charlson_sc$score < 5, "moderate", "severe"))

final_master <- final_master %>% merge(charlson_sc, by = "EMPI", all.x = TRUE)
```

## 5.15 Competing risk variables

```{r}
#| label: clean-competing-risk
# Apply cmp_variable() to build cmp_time_* and cmp_status_* for each outcome.
# AE outcomes (anemia, throm, aki, grade_2/3_aes) are now computed from RPDR pipeline
# (section 4.9) and their competing-risk variables are computed here.

# Adverse event competing risk
final_master <- cmp_variable(final_master, event_time = time_to_anemia_2, event_status = Anemia_g2_90days, name = "anemia_2")
final_master <- cmp_variable(final_master, event_time = time_to_anemia_3, event_status = Anemia_g3_90days, name = "anemia_3")
final_master <- cmp_variable(final_master, event_time = time_to_throm_2,  event_status = Throm_g2_90days,  name = "throm_2")
final_master <- cmp_variable(final_master, event_time = time_to_throm_3,  event_status = Throm_g3_90days,  name = "throm_3")
final_master <- cmp_variable(final_master, event_time = time_to_aki_2,    event_status = AKI_g2_90days,    name = "aki_2")
final_master <- cmp_variable(final_master, event_time = time_to_aki_3,    event_status = AKI_g3_90days,    name = "aki_3")
final_master <- cmp_variable(final_master, event_time = time_to_aki_kdigo, event_status = AKI_kdigo_90days, name = "aki_kdigo")
# Composite AE: use the earliest event time across anemia/throm/AKI
final_master <- final_master %>%
  mutate(
    time_to_grade_2_aes = pmin(time_to_anemia_2, time_to_throm_2, time_to_aki_2, na.rm = TRUE),
    time_to_grade_3_aes = pmin(time_to_anemia_3, time_to_throm_3, time_to_aki_3, na.rm = TRUE)
  )
final_master <- cmp_variable(final_master, event_time = time_to_grade_2_aes, event_status = grade_2_aes, name = "grade_2_aes")
final_master <- cmp_variable(final_master, event_time = time_to_grade_3_aes, event_status = grade_3_aes, name = "grade_3_aes")

# Platinum-related hospitalization (side effects: hosp reasons 1–7)
final_master <- cmp_variable(final_master,
  event_time = time_to_side_effect, event_status = side_effect, name = "side_effect")

# Hospitalization by reason 1–11
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_1,  event_status = event_hosp_1,  name = "hosp_1")
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_2,  event_status = event_hosp_2,  name = "hosp_2")
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_3,  event_status = event_hosp_3,  name = "hosp_3")
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_4,  event_status = event_hosp_4,  name = "hosp_4")
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_5,  event_status = event_hosp_5,  name = "hosp_5")
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_6,  event_status = event_hosp_6,  name = "hosp_6")
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_7,  event_status = event_hosp_7,  name = "hosp_7")
# hosp_8–11 use their own event_status
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_8,  event_status = event_hosp_8,  name = "hosp_8")
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_9,  event_status = event_hosp_9,  name = "hosp_9")
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_10, event_status = event_hosp_10, name = "hosp_10")
final_master <- cmp_variable(final_master, event_time = time_to_event_hosp_11, event_status = event_hosp_11, name = "hosp_11")

# Combined Immune-related AE (hosp_9) & Other (hosp_11): event = 1 if either
# occurred within 90 days, time = earliest of the two (90 if neither). All
# event/time variables already follow the convention "time = 90 if no event",
# so pmin() naturally yields the earliest event time when one or both occurred,
# and 90 when neither did.
final_master <- final_master %>%
  mutate(
    event_hosp_immune_other = pmax(event_hosp_9, event_hosp_11, na.rm = TRUE),
    time_to_event_hosp_immune_other = pmin(time_to_event_hosp_9,
                                           time_to_event_hosp_11, na.rm = TRUE)
  )
final_master <- cmp_variable(final_master,
  event_time = time_to_event_hosp_immune_other,
  event_status = event_hosp_immune_other,
  name = "hosp_immune_other")

# Overall hospitalization (any reason 1–11)
final_master <- cmp_variable(final_master,
  event_time = time_to_any_hosp, event_status = any_hosp, name = "any_hosp")

# Convert all cmp_status_* columns to factor (required by tidycmprsk)
final_master <- final_master %>%
  mutate(across(contains("cmp_status_"), as.factor))

# Drop record 911 — all RPDR pre-baseline labs are NA (see Section 6.1 note).
# This patient's nearest RPDR labs are ~189 days before baseline, well outside
# the 45-day pre_lab() window, so they are dropped from every Fine-Gray model
# via complete-case analysis anyway. Removing them up front keeps the cohort
# denominator consistent across tables and plots.
final_master <- final_master %>% filter(record_id != 911)

# --- Ritu cohort restriction: drop advanced/metastatic disease ---------------
# tumor_stage: 1 = Local/Early (stage I-II / local / neoadjuvant),
#              2 = Advanced/Metastatic (stage III-IV).
# Applied here, at the end of the pipeline, rather than at import. No derived
# variable above is defined relative to the cohort (there are no median splits,
# quantile categories, z-scores or imputation models), so restricting after
# derivation is numerically identical to restricting before it -- and it keeps
# this file line-for-line comparable with jiaxuan_data.qmd.
cat("Patients before stage restriction:", nrow(final_master), "\n")
print(table(final_master$tumor_stage, useNA = "ifany"))

final_master <- final_master %>%
  filter(tumor_stage == "Local/Early") %>%
  # Clear the now-empty Advanced/Metastatic level (and any covariate level left
  # with zero patients) so model matrices are not rank-deficient. cmp_status_*
  # factors are excluded: their 0/1/2 coding is relied on downstream.
  mutate(across(where(is.factor) & !starts_with("cmp_status_"), droplevels))

cat("Patients after stage restriction (Local/Early only):", nrow(final_master), "\n")
print(table(final_master$platin_group, useNA = "ifany"))

# Save final_master for use by ritu_whole.qmd / ritu_carbo.qmd / ritu_carbo_auc3.qmd
saveRDS(final_master, "ritu_final_master.rds")
```

# 6 Missing Data — Table 1 Variables

Variables that are NA by design for a platinum subgroup (`carbo_AUC`/`carbo_AUC_cat` for cisplatin patients; `cis_dose`/`cis_dose_cat` for carboplatin patients) are excluded from this table.

```{r}
#| label: ritu-missing-data
# Variables shared by all patients (not platinum-type-specific)
shared_vars <- c(
  "age", "age_cat", "sex", "race", "ethnicity", "cancer_type_cat_7",
  "platin_group",
  "ici", "Bevacizumab", "Paclitaxel", "Pemetrexed", "Doxorubicin", "Etoposide",
  "Gemcitabine", "Pertuzumab", "Trastuzumab", "Docetaxel", "Administered_alone",
  "hiv_rpdr", "thyroid", "smoking", "steroids",
  "cci", "ecog_score", "bmi", "bmi_cat",
  "pre_HGB_45days", "pre_PLT_45days", "pre_ALB_45days", "pre_CRE_45days",
  "baseline_cys_c", "baseline_cre", "cr_cys",
  "baseline_cre_egfr", "baseline_cys_c_egfr",
  "ckd_epi_gfr_cre_cys", "ckd_epi_gfr_cre_cys_unindex",
  "cockcroft"
)

# Shared variables: missing across all patients
shared_missing <- final_master %>%
  dplyr::select(any_of(shared_vars)) %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  tidyr::pivot_longer(everything(), names_to = "variable", values_to = "n_missing") %>%
  mutate(pct_missing = round(100 * n_missing / nrow(final_master), 1),
         note = "") %>%
  filter(n_missing > 0)

# Platinum-type-specific: check within their own subgroup
carbo_pts <- final_master %>% filter(platin_group == "Carboplatin")
cis_pts   <- final_master %>% filter(platin_group == "Cisplatin")

platin_missing <- tibble(
  variable   = c("carbo_AUC", "carbo_AUC_cat", "cis_dose", "cis_dose_cat"),
  n_missing  = c(sum(is.na(carbo_pts$carbo_AUC)),
                 sum(is.na(carbo_pts$carbo_AUC_cat)),
                 sum(is.na(cis_pts$cis_dose)),
                 sum(is.na(cis_pts$cis_dose_cat))),
  pct_missing = round(100 * n_missing /
                 c(nrow(carbo_pts), nrow(carbo_pts), nrow(cis_pts), nrow(cis_pts)), 1),
  note = c(paste0("of ", nrow(carbo_pts), " carbo pts"),
           paste0("of ", nrow(carbo_pts), " carbo pts"),
           paste0("of ", nrow(cis_pts), " cis pts"),
           paste0("of ", nrow(cis_pts), " cis pts"))
) %>% filter(n_missing > 0)

bind_rows(shared_missing, platin_missing) %>%
  arrange(desc(n_missing)) %>%
  knitr::kable(caption = "Missing data — Table 1 variables (non-zero only)")
```

## 6.1 Note: Record 911 — All RPDR Pre-Baseline Labs Missing

Record 911 (`baseline_sample_date` = 2025-08-19) has valid REDCap baseline labs
(`baseline_cre` = 0.93, `baseline_cys_c` = 0.88, `cockcroft` = 83.4) but **all
RPDR pre-baseline labs are NA** (`pre_HGB_45days`, `pre_PLT_45days`,
`pre_ALB_45days`, `pre_CRE_45days`).

**Root cause:** This patient has 73 RPDR lab records, but the closest labs before
baseline were drawn on 2025-02-11 — **189 days before baseline**, well outside the
45-day `pre_lab()` window. No RPDR labs exist between 2025-07-05 and 2025-08-19.

**Impact:** This patient is dropped from Fine-Gray models via complete-case
analysis whenever `pre_HGB_45days`, `pre_PLT_45days`, or `pre_CRE_45days` appears
as a covariate (i.e., all models except base-only AKI models). Their `cockcroft`,
`ckd_epi_gfr_cre_cys_unindex`, and `egfr_ratio` are valid.

