---
title: "Ritu Project — Carboplatin AUC ≥ 3 Cohort (Local/Early)"
author: "Tianqi Ouyang"
date: "2026-04-09"
execute:
  eval: true
  warning: false
  message: false
---

> **Ritu cohort — Local/Early stage only.** This page repeats the Jiaxuan carboplatin AUC ≥ 3 analysis on the subset of patients with `tumor_stage == "Local/Early"`, leaving **N = 143** patients. `tumor_stage` is dropped from Table 1 and from every adjuster set because it is constant within this cohort.
>
> **`steroids` is also dropped from the adjuster sets on this page only.** All 143 patients in this subgroup received steroids, so the variable is constant and collinear with the intercept. Together with an emptied `cancer_type_cat_7` "GI" level (cleared by `droplevels()` after the cohort filter) it made the design matrix rank-deficient, which caused `cmprsk::crr` to fail for *every* outcome regardless of event count. `steroids` is retained as a descriptive row in Table 1. The whole and carboplatin cohorts are full rank and keep the original adjuster set.
>
> **This is the sparsest of the three cohorts.** Against ~20 covariate degrees of freedom, only composite grade 2 AEs (64 events) and anemia grade 2 (62) are adequately powered. Two outcomes have **zero events** here: thrombocytopenia grade 3 — where Fine-Gray errors out and the sections below show a "model not estimable" note in place of the table or figure — and 90-day death, where Cox PH returns empty `NA` estimates rather than erroring. Neither carries any information. See `RITU_PROJECT.md`.

# 1 Setup

```{r}
#| label: setup-ritu-carbo
# Force UTF-8 locale so kable captions and other strings render real Unicode
# (e.g. em-dash) instead of <U+2014> escape sequences.
invisible(Sys.setlocale("LC_ALL", "en_US.UTF-8"))
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)
library(flextable)
library(rvg)
library(officer)
library(patchwork)

# Output directory for downloadable Word tables
docx_dir <- "docs/tables/auc3"
dir.create(docx_dir, recursive = TRUE, showWarnings = FALSE)

# Output directory for editable PowerPoint copies of every figure. A knitr
# plot hook (defined below) saves last_plot() to docs/pptx/auc3/<label>.pptx
# and appends a download link after the figure in the rendered HTML.
dir.create("docs/pptx/auc3", recursive = TRUE, showWarnings = FALSE)
pptx_dir <- normalizePath("docs/pptx/auc3", mustWork = TRUE)
pptx_rel_prefix <- "../pptx/auc3/"

.pptx_written <- new.env()
.pptx_pair    <- new.env()

.save_pptx <- function(p, path) {
  tryCatch({
    doc <- officer::read_pptx()
    doc <- officer::add_slide(doc, layout = "Title and Content",
                              master = "Office Theme")
    doc <- officer::ph_with(doc, rvg::dml(ggobj = p),
                            location = officer::ph_location_type(type = "body"))
    print(doc, target = path)
    TRUE
  }, error = function(e) FALSE)
}

knitr::opts_chunk$set(fig.process = function(filename) {
  label <- knitr::opts_current$get("label")
  if (is.null(label)) return(filename)
  pair <- .pptx_pair[[label]]
  if (!is.null(pair) && inherits(pair$default, "ggplot") && inherits(pair$fine, "ggplot")) {
    p1 <- file.path(pptx_dir, paste0(label, ".pptx"))
    p2 <- file.path(pptx_dir, paste0(label, "_10pct.pptx"))
    ok1 <- .save_pptx(pair$default, p1)
    ok2 <- .save_pptx(pair$fine,    p2)
    rels <- c(if (ok1) paste0(pptx_rel_prefix, label, ".pptx"),
              if (ok2) paste0(pptx_rel_prefix, label, "_10pct.pptx"))
    if (length(rels)) .pptx_written[[label]] <- rels
    return(filename)
  }
  p <- tryCatch(ggplot2::last_plot(), error = function(e) NULL)
  if (is.null(p) || !inherits(p, "ggplot")) return(filename)
  pptx_path <- file.path(pptx_dir, paste0(label, ".pptx"))
  if (.save_pptx(p, pptx_path)) {
    .pptx_written[[label]] <- paste0(pptx_rel_prefix, label, ".pptx")
  }
  filename
})

local({
  default_chunk_hook <- knitr::knit_hooks$get("chunk")
  knitr::knit_hooks$set(chunk = function(x, options) {
    out <- default_chunk_hook(x, options)
    label <- options$label
    if (!is.null(label) && !is.null(.pptx_written[[label]])) {
      rel <- .pptx_written[[label]]
      if (length(rel) == 2) {
        link <- sprintf(
          '\n\n<p style="margin-top:-0.5em;font-size:0.9em;"><a href="%s" download>📊 Download top plot as PowerPoint</a> · <a href="%s" download>📊 Download bottom (10 %% ticks)</a></p>\n\n',
          rel[1], rel[2])
      } else {
        link <- sprintf(
          '\n\n<p style="margin-top:-0.5em;font-size:0.9em;"><a href="%s" download>📊 Download as PowerPoint (editable)</a></p>\n\n',
          rel[1])
      }
      out <- paste0(out, link)
    }
    out
  })
})

# --- Sparse-outcome guard (Ritu cohort) --------------------------------------
# Restricting to Local/Early disease leaves several outcomes with very few
# events (90-day death = 2; thrombocytopenia grade 3 and the individual
# hospitalization reasons are in the single digits). A model that cannot be
# estimated raises an error, which would abort the entire render, so every
# table / row / figure helper is wrapped below. On success the output is exactly
# what the Jiaxuan version produces; on failure a short note is emitted in place
# of the table or figure. No model specification is changed.
.wrap_tbl <- function(f) {
  force(f)
  function(...) tryCatch(f(...), error = function(e) knitr::asis_output(paste0(
    "\n::: {.callout-warning}\n",
    "## Model not estimable in this cohort\n\n",
    "Too few events among the ", nrow(dat), " Local/Early patients to fit ",
    "this model with the full adjuster set.\n\n",
    "Error: `", conditionMessage(e), "`\n:::\n")))
}
.wrap_row <- function(f) {
  force(f)
  function(time_var, status_var, label, ...) tryCatch(
    f(time_var, status_var, label, ...),
    error = function(e) {
      ev <- tryCatch(
        sum(as.character(dat[[status_var]]) == "1", na.rm = TRUE),
        error = function(e2) NA_integer_)
      tibble::tibble(
        Outcome = label, Model = "not estimable",
        N = NA_integer_, `Excluded (missing cov.)` = NA_integer_,
        Events = as.integer(ev),
        `(sub)HR (95% CI)` = "not estimable", `p-value` = "\u2014")
    })
}
.wrap_plot <- function(f) {
  force(f)
  function(...) tryCatch(f(...), error = function(e)
    ggplot2::ggplot() +
      ggplot2::annotate("text", x = 0, y = 0, size = 3.4, lineheight = 1.3,
        label = paste0("Model not estimable in this cohort\n",
                       "(too few events among the ", nrow(dat),
                       " Local/Early patients)\n\n",
                       strwrap(conditionMessage(e), width = 60,
                               prefix = "\n", initial = ""))) +
      ggplot2::theme_void())
}

save_tbl_docx <- function(tbl, docx_name) {
  ft <- gtsummary::as_flex_table(tbl)
  flextable::save_as_docx(ft, path = file.path(docx_dir,
                                               paste0(docx_name, ".docx")))
  invisible(tbl)
}

# Load the Local/Early cohort, then keep only carboplatin patients
dat <- readRDS("ritu_final_master.rds") %>%
  filter(platin_group == "Carboplatin", carbo_AUC >= 3) %>%
  # Ritu: clear factor levels left empty by the cohort filter above,
  # so the model matrices stay full rank (cmp_status_* excluded --
  # their 0/1/2 coding is relied on downstream).
  mutate(across(where(is.factor) & !starts_with("cmp_status_"), droplevels))

# Create eGFR ratio: CKD-EPI Cr-Cys (unindexed) / Cockcroft-Gault
# Also create per-10 mL/min rescaled versions of cockcroft and CKD-EPI for
# reporting (HRs per 1 mL/min are clinically uninterpretable; convention in
# nephro-onc is per 10 mL/min — bio_agent confirmed). Adjusters keep raw scale.
dat <- dat %>%
  mutate(
    # Capped versions (for dose discrepancy calculations)
    cockcroft_cap125 = pmin(cockcroft, 125),
    # ckd_epi_gfr_cre_cys_unindex_cap125 already exists in data
    # Ratio uses UNCAPPED eGFR
    egfr_ratio    = ckd_epi_gfr_cre_cys_unindex / cockcroft,
    egfr_ratio_per10 = -egfr_ratio * 10,  # per 0.1-unit *decrease* reporting scale
    egfr_discrepancy = ckd_epi_gfr_cre_cys_unindex - cockcroft,
    # per-10-mL/min DECLINE reporting scale for eGFR discrepancy: HR for this
    # variable reads as the multiplicative change in subHR per 10 mL/min lower
    # discrepancy (i.e., when CKD-EPI Cr-Cys is 10 mL/min farther below CG).
    egfr_disc_per10dec = -egfr_discrepancy / 10,
    # Sensitivity-analysis eGFR ratio (Section 16):
    # numerator = CKD-EPI 2012 cystatin C only (baseline_cys_c_egfr_unindexed)
    # denominator = CKD-EPI 2021 race-free creatinine only (baseline_cre_egfr_unindexed)
    # per10 below is the per-0.1 DECLINE reporting scale.
    egfr_ratio_sens       = baseline_cys_c_egfr_unindexed / baseline_cre_egfr_unindexed,
    egfr_ratio_sens_per10 = -egfr_ratio_sens * 10,
    # Percent-difference eGFR (new primary exposure):
    # egfr_diff_pct = 100 * (CKD-EPI Cr-Cys unindexed - Cockcroft-Gault) / Cockcroft-Gault
    # egfr_diff_pct_per10: HR reads as multiplicative change per 10 percentage-point DECLINE.
    egfr_diff_pct         = 100 * (ckd_epi_gfr_cre_cys_unindex - cockcroft) / cockcroft,
    egfr_diff_pct_per10   = -egfr_diff_pct / 10,
    # Percent-difference eGFR for sensitivity analysis:
    # numerator - denominator = CKD-EPI 2012 CysC - CKD-EPI 2021 Cr, both unindexed.
    egfr_diff_pct_sens        = 100 * (baseline_cys_c_egfr_unindexed - baseline_cre_egfr_unindexed) / baseline_cre_egfr_unindexed,
    egfr_diff_pct_sens_per10  = -egfr_diff_pct_sens / 10,
    # Dose discrepancy uses CAPPED eGFR (already computed in ritu_data.qmd)
    dose_discrep_per25increase = dose_discrepancy / 25,
    abs_dose_discrep = abs(dose_discrepancy),
    abs_dose_discrep_cat = cut(abs_dose_discrep,
      breaks = c(0, 25, 50, 75, 100, Inf),
      labels = c("<25", "25-49.99", "50-74.99", "75-99.99", ">=100"),
      right = FALSE, include.lowest = TRUE),
    # Binary exposure for adjusted CIF curves (Section 14): 1 if patient was
    # over-dosed by 25 mg or more (actual - predicted >= 25), else 0.
    dose_discrep_ge25 = as.integer(dose_discrepancy >= 25),
    # Signed dose discrepancy = actual - predicted; 10 bins symmetric around 0.
    signed_dose_discrep_cat = cut(dose_discrepancy,
      breaks = c(-Inf, -100, -75, -50, -25, 0, 25, 50, 75, 100, Inf),
      labels = c("<=-100", "-99.99 to -75", "-74.99 to -50",
                 "-49.99 to -25", "-24.99 to 0",
                 "0 to 24.99", "25 to 49.99", "50 to 74.99",
                 "75 to 99.99", ">=100"),
      right = FALSE, include.lowest = TRUE),
    cockcroft_per10 = cockcroft / 10,
    ckd_epi_per10   = ckd_epi_gfr_cre_cys_unindex / 10
  )

cat("Carboplatin AUC >= 3 cohort N =", nrow(dat), "\n")
```

# 2 Actual vs Predicted Dose (Carboplatin AUC ≥ 3)

```{r}
#| label: ritu-auc3-dose-overlay
#| fig-width: 8
#| fig-height: 5
dose_long <- dat %>%
  select(record_id, carbo_dose_redcap, carbo_dose_cre_cys) %>%
  pivot_longer(
    cols = c(carbo_dose_redcap, carbo_dose_cre_cys),
    names_to = "dose_type", values_to = "dose_mg"
  ) %>%
  filter(!is.na(dose_mg)) %>%
  mutate(dose_type = case_match(dose_type,
    "carbo_dose_redcap"  ~ "Actual (REDCap)",
    "carbo_dose_cre_cys" ~ "Predicted (CKD-EPI Cr-Cys)"
  ))

ggplot(dose_long, aes(x = dose_mg, fill = dose_type)) +
  geom_histogram(alpha = 0.5, bins = 40, position = "identity", color = "black") +
  scale_fill_manual(values = c("Actual (REDCap)" = "#E31A1C",
                                "Predicted (CKD-EPI Cr-Cys)" = "#1F78B4")) +
  labs(title = "Carboplatin Dose Distribution (AUC ≥ 3)",
       x = "Dose (mg)", y = "Number of Patients", fill = "Dose Type") +
  theme_minimal(base_size = 14)
```

Smoothed kernel-density version of the same two distributions (Actual REDCap dose in red, CKD-EPI Cr-Cys–predicted Calvert dose in blue). Easier to see location / spread differences without the histogram jitter.

```{r}
#| label: ritu-auc3-dose-overlay-density
#| fig-width: 8
#| fig-height: 5
ggplot(dose_long, aes(x = dose_mg, fill = dose_type, color = dose_type)) +
  geom_density(alpha = 0.35, linewidth = 0.9) +
  scale_fill_manual(values = c("Actual (REDCap)" = "#E31A1C",
                                "Predicted (CKD-EPI Cr-Cys)" = "#1F78B4")) +
  scale_color_manual(values = c("Actual (REDCap)" = "#E31A1C",
                                 "Predicted (CKD-EPI Cr-Cys)" = "#1F78B4")) +
  labs(title = "Carboplatin Dose Distribution (AUC ≥ 3) — density",
       x = "Dose (mg)", y = "Density",
       fill = "Dose Type", color = "Dose Type") +
  theme_minimal(base_size = 14)
```

## 2.2 Signed Dose Discrepancy Distribution

Smooth kernel density estimate of the signed dose discrepancy (actual − predicted, CKD-EPI Cr-Cys). The area under the curve is shaded by sign — negative (under-dosed region) on one side, positive on the other.

```{r}
#| label: ritu-auc3-dose-discrep-hist
#| fig-width: 9
#| fig-height: 5
dose_vals <- dat %>%
  filter(!is.na(dose_discrepancy)) %>%
  pull(dose_discrepancy)

dens <- density(dose_vals, n = 512)
y_at_zero <- approx(dens$x, dens$y, xout = 0)$y

dens_df <- tibble(x = dens$x, y = dens$y) %>%
  bind_rows(tibble(x = 0, y = y_at_zero)) %>%
  arrange(x)

neg_part <- dens_df %>% filter(x <= 0) %>% mutate(side = "neg")
pos_part <- dens_df %>% filter(x >= 0) %>% mutate(side = "pos")
plot_df  <- bind_rows(neg_part, pos_part)

ggplot() +
  geom_area(data = plot_df, aes(x = x, y = y, fill = side), alpha = 0.6) +
  geom_line(data = dens_df, aes(x = x, y = y), linewidth = 0.6, color = "black") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey40") +
  geom_vline(xintercept = 25, linetype = "dotted", color = "grey30") +
  scale_fill_manual(values = c(neg = "#E31A1C", pos = "grey60"),
                    guide = "none") +
  coord_cartesian(xlim = c(-250, 250), ylim = c(0, 0.010)) +
  labs(title = "Distribution of Signed Dose Discrepancy (Carboplatin AUC ≥ 3)",
       x = "Dose Discrepancy (mg) = Actual dose – Predicted dose",
       y = "Density") +
  theme_minimal(base_size = 13)
```

# 3 Table 1: Baseline Characteristics (Carboplatin AUC ≥ 3)

```{r}
#| label: ritu-table1-carbo
dat %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, cancer_type_cat_7,
    carbo_AUC, carbo_AUC_cat,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, other_chemo, Administered_alone,
    hiv_rpdr, thyroid, smoking, steroids,
    cci, score, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days, pre_CRE_45days,
    baseline_cys_c, baseline_cre, cr_cys,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    cockcroft, egfr_ratio
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
```

## 3.1 Follow-up time (days from baseline to last known status)

Four alternative definitions of follow-up time shown side-by-side:

- **A — Raw days**: unrestricted calendar follow-up (median dominated by patients who kept returning for years).
- **B — Raw days, ≤ 365 days**: restricts to patients whose last-known contact was within 1 year of baseline.
- **C — Analytic, capped at 90 days**: `min(days_last_follow_up, 90)` — actual risk time in the 90-day models.
- **D — Analytic (capped at 90) & ≤ 365 days raw**: same as C but excluding long-tail returners.

```{r}
#| label: ritu-auc3-followup-desc
followup_summary <- dat %>%
  dplyr::select(record_id, days_last_follow_up) %>%
  tidyr::drop_na(days_last_follow_up)

fmt_med_iqr <- function(x) {
  if (length(x) == 0) return("—")
  sprintf("%.0f [%.0f, %.0f]", median(x), quantile(x, 0.25), quantile(x, 0.75))
}

fu_row <- function(label, v) {
  tibble::tibble(
    Interpretation                  = label,
    N                               = length(v),
    `Median [IQR] follow-up (days)` = fmt_med_iqr(v)
  )
}

v <- followup_summary$days_last_follow_up
followup_tbl <- dplyr::bind_rows(
  fu_row("A — Raw days",                                 v),
  fu_row("B — Raw days, ≤ 365 days",                     v[v <= 365]),
  fu_row("C — Analytic (capped at 90 days)",             pmin(v, 90)),
  fu_row("D — Analytic (capped at 90 days), ≤ 365 days", pmin(v[v <= 365], 90))
)

flextable::flextable(followup_tbl) |>
  flextable::set_caption("Follow-up time from baseline to last known status (Carboplatin AUC ≥ 3 cohort). Four alternative definitions.") |>
  flextable::autofit()
```

# 4 eGFR Ratio Distribution (Carboplatin AUC ≥ 3)

```{r}
#| label: ritu-auc3-egfr-ratio-hist
#| fig-width: 8
#| fig-height: 5
ratio_hist <- dat %>%
  filter(!is.na(egfr_ratio)) %>%
  mutate(side = ifelse(egfr_ratio < 1, "neg", "pos"))

ggplot(ratio_hist, aes(x = egfr_ratio, fill = side)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count)) * 100),
                 binwidth = 0.1, boundary = 0,
                 color = "black", alpha = 0.85) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey30") +
  scale_fill_manual(values = c(neg = "#E31A1C", pos = "grey60"),
                    guide = "none") +
  labs(title = "Distribution of eGFR Ratio (Carboplatin AUC ≥ 3)",
       x = "eGFR Ratio",
       y = "Percent of Patients (%)") +
  scale_x_continuous(breaks = seq(0, 3, 0.2)) +
  theme_minimal(base_size = 14)
```

# 5 Fine-Gray Models — eGFR Difference (%) (per 10 % decline, adjusted for Cockcroft-Gault) (Carboplatin AUC ≥ 3)

Each table below shows univariable (one variable at a time) and multivariable Fine-Gray subdistribution hazard ratios side-by-side. A Word version of every table is saved during render — click any link below to download:

- [Anemia Grade 2](../tables/auc3/sec5_anemia_2.docx) · [Anemia Grade 3](../tables/auc3/sec5_anemia_3.docx)
- [Thrombocytopenia Grade 2](../tables/auc3/sec5_throm_2.docx) · [Thrombocytopenia Grade 3](../tables/auc3/sec5_throm_3.docx)
- [AKI Grade 2](../tables/auc3/sec5_aki_2.docx) · [AKI (KDIGO)](../tables/auc3/sec5_aki_kdigo.docx)
- [Composite Grade 2 AEs](../tables/auc3/sec5_grade_2_aes.docx) · [Composite Grade 3 AEs](../tables/auc3/sec5_grade_3_aes.docx)
- [Overall Hospitalization](../tables/auc3/sec5_any_hosp.docx) · [Platinum-Related Hospitalization](../tables/auc3/sec5_side_effect.docx)
- [90-Day Death (Cox PH)](../tables/auc3/sec5_death_90.docx)

```{r}
#| label: ritu-auc3-fg-helper
.adj_set <- function(pre_labs, egfr_adj) {
  adj <- c("age","sex","score","ecog_score_cat2",
           "cancer_type_cat_7","high_dose",
           "Paclitaxel","Pemetrexed","Gemcitabine","ici",
           "bmi","smoking","thyroid")
  if (egfr_adj == "cockcroft") adj <- c(adj, "cockcroft")
  if (egfr_adj == "ckd_epi")   adj <- c(adj, "ckd_epi_gfr_cre_cys_unindex")
  if (!is.null(pre_labs)) adj <- c(adj, pre_labs)
  adj
}

# fg_model: returns univariable + multivariable merged Fine-Gray table.
# If docx_name is supplied, also saves the table as a .docx in docx_dir.
fg_model <- function(time_var, status_var, pred_var, pre_labs = NULL,
                     egfr_adj = c("none", "cockcroft", "ckd_epi"),
                     docx_name = NULL) {
  egfr_adj <- match.arg(egfr_adj)
  adj <- .adj_set(pre_labs, egfr_adj)
  all_vars <- c(pred_var, adj)

  fmla_mv <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(all_vars, collapse = " + ")
  ))
  tbl_mv <- tidycmprsk::crr(fmla_mv, failcode = 1, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()

  y_call <- str2lang(sprintf("Surv(%s, %s)", time_var, status_var))
  tbl_uv <- rlang::inject(
    tbl_uvregression(
      data = dat,
      method = tidycmprsk::crr,
      y = !!y_call,
      include = dplyr::all_of(all_vars),
      exponentiate = TRUE,
      pvalue_fun = function(x) style_pvalue(x, digits = 3),
      method.args = list(failcode = 1)
    )
  )

  out <- tbl_merge(
    tbls = list(tbl_uv, tbl_mv),
    tab_spanner = c("**Univariable**", "**Multivariable**")
  )

  if (!is.null(docx_name)) save_tbl_docx(out, docx_name)
  out
}
# Ritu: guard against unfittable sparse-outcome models.
fg_model <- .wrap_tbl(fg_model)


cox_model <- function(time_var, status_var, pred_var, pre_labs = NULL,
                      egfr_adj = c("none", "cockcroft", "ckd_epi"),
                      docx_name = NULL) {
  egfr_adj <- match.arg(egfr_adj)
  adj <- .adj_set(pre_labs, egfr_adj)
  all_vars <- c(pred_var, adj)

  fmla_mv <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(all_vars, collapse = " + ")
  ))
  tbl_mv <- survival::coxph(fmla_mv, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()

  y_call <- str2lang(sprintf("Surv(%s, %s)", time_var, status_var))
  tbl_uv <- rlang::inject(
    tbl_uvregression(
      data = dat,
      method = survival::coxph,
      y = !!y_call,
      include = dplyr::all_of(all_vars),
      exponentiate = TRUE,
      pvalue_fun = function(x) style_pvalue(x, digits = 3)
    )
  )

  out <- tbl_merge(
    tbls = list(tbl_uv, tbl_mv),
    tab_spanner = c("**Univariable**", "**Multivariable**")
  )

  if (!is.null(docx_name)) save_tbl_docx(out, docx_name)
  out
}
# Ritu: guard against unfittable sparse-outcome models.
cox_model <- .wrap_tbl(cox_model)

```

## 4.1 Anemia Grade 2

```{r}
#| label: ritu-auc3-fg-cg-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_diff_pct_per10", "pre_HGB_45days", "cockcroft", docx_name = "sec5_anemia_2")
```

## 4.2 Anemia Grade 3

```{r}
#| label: ritu-auc3-fg-cg-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_diff_pct_per10", "pre_HGB_45days", "cockcroft", docx_name = "sec5_anemia_3")
```

## 4.3 Thrombocytopenia Grade 2

```{r}
#| label: ritu-auc3-fg-cg-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "egfr_diff_pct_per10", "pre_PLT_45days", "cockcroft", docx_name = "sec5_throm_2")
```

## 4.4 Thrombocytopenia Grade 3

```{r}
#| label: ritu-auc3-fg-cg-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "egfr_diff_pct_per10", "pre_PLT_45days", "cockcroft", docx_name = "sec5_throm_3")
```

## 4.5 AKI Grade 2

```{r}
#| label: ritu-auc3-fg-cg-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "egfr_diff_pct_per10", egfr_adj = "cockcroft", docx_name = "sec5_aki_2")
```

## 4.6 AKI (KDIGO)

```{r}
#| label: ritu-auc3-fg-cg-akikdigo
fg_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "egfr_diff_pct_per10", egfr_adj = "cockcroft", docx_name = "sec5_aki_kdigo")
```

## 4.7 Composite Grade 2 AEs

```{r}
#| label: ritu-auc3-fg-cg-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "egfr_diff_pct_per10", egfr_adj = "cockcroft", docx_name = "sec5_grade_2_aes")
```

## 4.8 Composite Grade 3 AEs

```{r}
#| label: ritu-auc3-fg-cg-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "egfr_diff_pct_per10", egfr_adj = "cockcroft", docx_name = "sec5_grade_3_aes")
```

## 4.9 Overall Hospitalization

```{r}
#| label: ritu-auc3-fg-cg-anyhosp
fg_model("cmp_time_any_hosp", "cmp_status_any_hosp", "egfr_diff_pct_per10", egfr_adj = "cockcroft", docx_name = "sec5_any_hosp")
```

## 4.10 Platinum-Related Hospitalization

```{r}
#| label: ritu-auc3-fg-cg-sideeffect
fg_model("cmp_time_side_effect", "cmp_status_side_effect", "egfr_diff_pct_per10", egfr_adj = "cockcroft", docx_name = "sec5_side_effect")
```

## 4.11 90-Day Death (Cox PH)

```{r}
#| label: ritu-auc3-cox-cg-death
cox_model("time_to_death_90", "death_90", "egfr_diff_pct_per10", egfr_adj = "cockcroft", docx_name = "sec5_death_90")
```

# 6 Cause-Specific Hazard Models — eGFR Difference (%) (per 10 % decline, adjusted for Cockcroft-Gault) (Carboplatin AUC ≥ 3)

```{r}
#| label: ritu-auc3-csh-helper
csh_model <- function(time_var, status_var, pred_var, pre_labs = NULL) {
  adj <- c("age","sex","score","ecog_score_cat2",
           "cancer_type_cat_7","high_dose",
           "Paclitaxel","Pemetrexed","Gemcitabine","ici",
           "bmi","smoking","thyroid","cockcroft")
  if (!is.null(pre_labs)) adj <- c(adj, pre_labs)
  d <- dat
  d$csh_status <- ifelse(d[[status_var]] == 1, 1L, 0L)
  fmla <- as.formula(paste0(
    "Surv(", time_var, ", csh_status) ~ ",
    paste(c(pred_var, adj), collapse = " + ")
  ))
  survival::coxph(fmla, data = d) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()
}
# Ritu: guard against unfittable sparse-outcome models.
csh_model <- .wrap_tbl(csh_model)

```

## 5.1 Anemia Grade 2

```{r}
#| label: ritu-auc3-csh-anemia2
csh_model("cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_diff_pct_per10", "pre_HGB_45days")
```

## 5.2 Anemia Grade 3

```{r}
#| label: ritu-auc3-csh-anemia3
csh_model("cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_diff_pct_per10", "pre_HGB_45days")
```

## 5.3 Thrombocytopenia Grade 2

```{r}
#| label: ritu-auc3-csh-throm2
csh_model("cmp_time_throm_2", "cmp_status_throm_2", "egfr_diff_pct_per10", "pre_PLT_45days")
```

## 5.4 Thrombocytopenia Grade 3

```{r}
#| label: ritu-auc3-csh-throm3
csh_model("cmp_time_throm_3", "cmp_status_throm_3", "egfr_diff_pct_per10", "pre_PLT_45days")
```

## 5.5 AKI Grade 2

```{r}
#| label: ritu-auc3-csh-aki2
csh_model("cmp_time_aki_2", "cmp_status_aki_2", "egfr_diff_pct_per10")
```

## 5.6 AKI (KDIGO)

```{r}
#| label: ritu-auc3-csh-akikdigo
csh_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "egfr_diff_pct_per10")
```

## 5.7 Composite Grade 2 AEs

```{r}
#| label: ritu-auc3-csh-grade2
csh_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "egfr_diff_pct_per10")
```

## 5.8 Composite Grade 3 AEs

```{r}
#| label: ritu-auc3-csh-grade3
csh_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "egfr_diff_pct_per10")
```

## 5.9 Overall Hospitalization

```{r}
#| label: ritu-auc3-csh-anyhosp
csh_model("cmp_time_any_hosp", "cmp_status_any_hosp", "egfr_diff_pct_per10")
```

## 5.10 Platinum-Related Hospitalization

```{r}
#| label: ritu-auc3-csh-sideeffect
csh_model("cmp_time_side_effect", "cmp_status_side_effect", "egfr_diff_pct_per10")
```

## 5.11 90-Day Death (Cox PH)

```{r}
#| label: ritu-auc3-csh-death
cox_model("time_to_death_90", "death_90", "egfr_diff_pct_per10", egfr_adj = "cockcroft")
```

# 7 Fine-Gray Models — Dose Discrepancy per 25 mg (adjusted for Cockcroft-Gault) (Carboplatin AUC ≥ 3)

## 6.1 Anemia Grade 2

```{r}
#| label: ritu-auc3-fg-dd-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "dose_discrep_per25increase", "pre_HGB_45days", "cockcroft")
```

## 6.2 Anemia Grade 3

```{r}
#| label: ritu-auc3-fg-dd-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "dose_discrep_per25increase", "pre_HGB_45days", "cockcroft")
```

## 6.3 Thrombocytopenia Grade 2

```{r}
#| label: ritu-auc3-fg-dd-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "dose_discrep_per25increase", "pre_PLT_45days", "cockcroft")
```

## 6.4 Thrombocytopenia Grade 3

```{r}
#| label: ritu-auc3-fg-dd-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "dose_discrep_per25increase", "pre_PLT_45days", "cockcroft")
```

## 6.5 AKI Grade 2

```{r}
#| label: ritu-auc3-fg-dd-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 6.6 AKI (KDIGO)

```{r}
#| label: ritu-auc3-fg-dd-akikdigo
fg_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 6.7 Composite Grade 2 AEs

```{r}
#| label: ritu-auc3-fg-dd-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 6.8 Composite Grade 3 AEs

```{r}
#| label: ritu-auc3-fg-dd-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 6.9 Overall Hospitalization

```{r}
#| label: ritu-auc3-fg-dd-anyhosp
fg_model("cmp_time_any_hosp", "cmp_status_any_hosp", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 6.10 Platinum-Related Hospitalization

```{r}
#| label: ritu-auc3-fg-dd-sideeffect
fg_model("cmp_time_side_effect", "cmp_status_side_effect", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

## 6.11 90-Day Death (Cox PH)

```{r}
#| label: ritu-auc3-cox-dd-death
cox_model("time_to_death_90", "death_90", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

# 8 Cause-Specific Hazard Models — Dose Discrepancy per 25 mg (adjusted for Cockcroft-Gault) (Carboplatin AUC ≥ 3)

## 7.1 Anemia Grade 2

```{r}
#| label: ritu-auc3-csh-dd-anemia2
csh_model("cmp_time_anemia_2", "cmp_status_anemia_2", "dose_discrep_per25increase", "pre_HGB_45days")
```

## 7.2 Anemia Grade 3

```{r}
#| label: ritu-auc3-csh-dd-anemia3
csh_model("cmp_time_anemia_3", "cmp_status_anemia_3", "dose_discrep_per25increase", "pre_HGB_45days")
```

## 7.3 Thrombocytopenia Grade 2

```{r}
#| label: ritu-auc3-csh-dd-throm2
csh_model("cmp_time_throm_2", "cmp_status_throm_2", "dose_discrep_per25increase", "pre_PLT_45days")
```

## 7.4 Thrombocytopenia Grade 3

```{r}
#| label: ritu-auc3-csh-dd-throm3
csh_model("cmp_time_throm_3", "cmp_status_throm_3", "dose_discrep_per25increase", "pre_PLT_45days")
```

## 7.5 AKI Grade 2

```{r}
#| label: ritu-auc3-csh-dd-aki2
csh_model("cmp_time_aki_2", "cmp_status_aki_2", "dose_discrep_per25increase")
```

## 7.6 AKI (KDIGO)

```{r}
#| label: ritu-auc3-csh-dd-akikdigo
csh_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "dose_discrep_per25increase")
```

## 7.7 Composite Grade 2 AEs

```{r}
#| label: ritu-auc3-csh-dd-grade2
csh_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "dose_discrep_per25increase")
```

## 7.8 Composite Grade 3 AEs

```{r}
#| label: ritu-auc3-csh-dd-grade3
csh_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "dose_discrep_per25increase")
```

## 7.9 Overall Hospitalization

```{r}
#| label: ritu-auc3-csh-dd-anyhosp
csh_model("cmp_time_any_hosp", "cmp_status_any_hosp", "dose_discrep_per25increase")
```

## 7.10 Platinum-Related Hospitalization

```{r}
#| label: ritu-auc3-csh-dd-sideeffect
csh_model("cmp_time_side_effect", "cmp_status_side_effect", "dose_discrep_per25increase")
```

## 7.11 90-Day Death (Cox PH)

```{r}
#| label: ritu-auc3-csh-dd-death
cox_model("time_to_death_90", "death_90", "dose_discrep_per25increase", egfr_adj = "cockcroft")
```

::: {.callout-note}
## Why anchor at the median (subHR = 1 at the reference)

Three reasons to anchor at the **median**:

1. **Interpretability**: "A patient with eGFR ratio of 0.8 has ~1.5× the subHR compared to a typical patient (at the median)."
2. **Stability**: The median sits in the densest part of the data, so estimates near it have the tightest confidence intervals. The CIs fan out as you move away — you can see this in the plots.
3. **No arbitrary choice**: If we picked 1.0 arbitrarily, the plot would look almost identical here (because median ≈ 1), but in cohorts where the median is 0.9 or 1.1, picking 1.0 would either shift or distort the curve without changing the actual model.
:::

# 9 Linear subHR Curves — eGFR Difference (%) (raw scale) (Carboplatin AUC ≥ 3)

::: {.callout-note}
## p-value convention

The p-value shown in each panel subtitle below is **Bonferroni-adjusted** across the six primary manuscript-figure AE outcomes (platinum-related hospitalisation, overall hospitalisation, 90-day mortality, grade ≥ 3 anemia, grade ≥ 3 thrombocytopenia, acute kidney injury): `p_Bonf = min(raw p × 6, 1)`. `n = 6` is displayed alongside for transparency. Raw Wald p is preserved in the Section 5 regression tables and their downloadable Word versions.
:::

```{r}
#| label: ritu-auc3-linsubhr-ratio-helper
plot_subhr_linear_ratio <- function(time_var, status_var, extra_adj = NULL,
                                    outcome_label, n_bonf = 6) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  keep <- c("egfr_diff_pct", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_diff_pct = d$egfr_diff_pct, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]
  se_b   <- sqrt(V_beta)

  q1    <- as.numeric(quantile(d$egfr_diff_pct, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_diff_pct, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  hr10  <- exp(-10 * beta);     hr10_l <- exp(-10 * beta - 1.96 * 10 * se_b);   hr10_u <- exp(-10 * beta + 1.96 * 10 * se_b)
  hri   <- exp(-iqr_w * beta);   hri_l  <- exp(-iqr_w * beta - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(-iqr_w * beta + 1.96 * abs(iqr_w) * se_b)
  pval  <- 2 * (1 - pnorm(abs(beta / se_b)))
  pval_bonf <- min(pval * n_bonf, 1)
  p_shown <- if (n_bonf > 1) pval_bonf else pval
  p_lbl   <- if (n_bonf > 1) sprintf("p_Bonf = %s (n = %d)", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)), n_bonf) else sprintf("p = %s", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)))
  subtitle_str <- sprintf(
    "subHR per 10 %% decline: %.2f (%.2f-%.2f), %s  |  per IQR decline (Δ = %.1f %%): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f] %%",
    hr10, hr10_l, hr10_u, p_lbl, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_diff_pct, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_diff_pct, 0.025, na.rm = TRUE),
                quantile(d$egfr_diff_pct, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  p <- ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "eGFR difference (%): 100 × (CKD-EPI Cr-Cys − CG) / CG",
         y = "subHR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25"))
  p_fine <- p + scale_x_continuous(breaks = seq(-100, 200, 10))
  .lbl <- tryCatch(knitr::opts_current$get("label"), error = function(e) NULL)
  if (!is.null(.lbl)) .pptx_pair[[.lbl]] <- list(default = p, fine = p_fine)
  p / p_fine
}
# Ritu: guard against unfittable sparse-outcome models.
plot_subhr_linear_ratio <- .wrap_plot(plot_subhr_linear_ratio)


plot_cox_linear_ratio <- function(time_var, status_var, extra_adj = NULL,
                                  outcome_label, n_bonf = 6) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  keep <- c("egfr_diff_pct", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ egfr_diff_pct + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- survival::coxph(fmla, data = d)

  beta   <- coef(fit)["egfr_diff_pct"]
  V_beta <- vcov(fit)["egfr_diff_pct", "egfr_diff_pct"]
  se_b   <- sqrt(V_beta)

  q1    <- as.numeric(quantile(d$egfr_diff_pct, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_diff_pct, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  hr10  <- exp(-10 * beta);     hr10_l <- exp(-10 * beta - 1.96 * 10 * se_b);   hr10_u <- exp(-10 * beta + 1.96 * 10 * se_b)
  hri   <- exp(-iqr_w * beta);   hri_l  <- exp(-iqr_w * beta - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(-iqr_w * beta + 1.96 * abs(iqr_w) * se_b)
  pval  <- 2 * (1 - pnorm(abs(beta / se_b)))
  pval_bonf <- min(pval * n_bonf, 1)
  p_shown <- if (n_bonf > 1) pval_bonf else pval
  p_lbl   <- if (n_bonf > 1) sprintf("p_Bonf = %s (n = %d)", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)), n_bonf) else sprintf("p = %s", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)))
  subtitle_str <- sprintf(
    "HR per 10 %% decline: %.2f (%.2f-%.2f), %s  |  per IQR decline (Δ = %.1f %%): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f] %%",
    hr10, hr10_l, hr10_u, p_lbl, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_diff_pct, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_diff_pct, 0.025, na.rm = TRUE),
                quantile(d$egfr_diff_pct, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x   = grid_x,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  p <- ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "eGFR difference (%): 100 × (CKD-EPI Cr-Cys − CG) / CG",
         y = "HR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25"))
  p_fine <- p + scale_x_continuous(breaks = seq(-100, 200, 10))
  .lbl <- tryCatch(knitr::opts_current$get("label"), error = function(e) NULL)
  if (!is.null(.lbl)) .pptx_pair[[.lbl]] <- list(default = p, fine = p_fine)
  p / p_fine
}
# Ritu: guard against unfittable sparse-outcome models.
plot_cox_linear_ratio <- .wrap_plot(plot_cox_linear_ratio)

```

## 8.1 Anemia Grade 2

```{r}
#| label: ritu-auc3-linsubhr-ratio-anemia2
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_anemia_2", "cmp_status_anemia_2",
                        "pre_HGB_45days", "Anemia Grade 2 (Carboplatin AUC ≥ 3)")
```

## 8.2 Anemia Grade 3

```{r}
#| label: ritu-auc3-linsubhr-ratio-anemia3
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_anemia_3", "cmp_status_anemia_3",
                        "pre_HGB_45days", "Anemia Grade 3 (Carboplatin AUC ≥ 3)")
```

## 8.3 Thrombocytopenia Grade 2

```{r}
#| label: ritu-auc3-linsubhr-ratio-throm2
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_throm_2", "cmp_status_throm_2",
                        "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin AUC ≥ 3)")
```

## 8.4 Thrombocytopenia Grade 3

```{r}
#| label: ritu-auc3-linsubhr-ratio-throm3
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_throm_3", "cmp_status_throm_3",
                        "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin AUC ≥ 3)")
```

## 8.5 AKI Grade 2

```{r}
#| label: ritu-auc3-linsubhr-ratio-aki2
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_aki_2", "cmp_status_aki_2",
                        NULL, "AKI Grade 2 (Carboplatin AUC ≥ 3)")
```

## 8.6 AKI (KDIGO)

```{r}
#| label: ritu-auc3-linsubhr-ratio-akikdigo
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                        NULL, "AKI (KDIGO) (Carboplatin AUC ≥ 3)")
```

## 8.7 Composite Grade 2 AEs

```{r}
#| label: ritu-auc3-linsubhr-ratio-grade2
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                        NULL, "Composite Grade 2 AEs (Carboplatin AUC ≥ 3)")
```

## 8.8 Composite Grade 3 AEs

```{r}
#| label: ritu-auc3-linsubhr-ratio-grade3
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                        NULL, "Composite Grade 3 AEs (Carboplatin AUC ≥ 3)")
```

## 8.9 Overall Hospitalization

```{r}
#| label: ritu-auc3-linsubhr-ratio-anyhosp
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_any_hosp", "cmp_status_any_hosp",
                        NULL, "Overall Hospitalization (Carboplatin AUC ≥ 3)")
```

## 8.10 Platinum-Related Hospitalization

```{r}
#| label: ritu-auc3-linsubhr-ratio-sideeffect
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_side_effect", "cmp_status_side_effect",
                        NULL, "Platinum-Related Hospitalization (Carboplatin AUC ≥ 3)")
```

## 8.11 90-Day Death (Cox PH)

```{r}
#| label: ritu-auc3-cox-linear-ratio-death
#| fig-width: 6
#| fig-height: 8
plot_cox_linear_ratio("time_to_death_90", "death_90",
                      NULL, "90-Day Death (Cox PH) (Carboplatin AUC ≥ 3)")
```

# 10 Linear subHR Curves — eGFR Discrepancy (raw scale) (Carboplatin AUC ≥ 3)

## 10.0 Summary table: Fine-Gray subHR per 10 mL/min decline in eGFR discrepancy

One row per outcome. Multivariable Fine-Gray model fit with `egfr_disc_per10dec = -egfr_discrepancy / 10` (positive when CKD-EPI Cr-Cys is below CG) plus the same adjusters used by the curves below (no `platin_group` in the AUC ≥ 3 cohort). The HR for `egfr_disc_per10dec` is the multiplicative change in subHR per **10 mL/min lower** eGFR discrepancy. 90-day death uses Cox PH. p-values in this summary table are **raw Wald** (not Bonferroni-adjusted); the plot subtitles in Sections 10.1–10.11 apply Bonferroni correction across the six primary AE outcomes.

[📄 Download Word table](../tables/auc3/sec10_disc_summary.docx)

```{r}
#| label: ritu-auc3-fg-disc-summary
.disc_adj_set <- function(pre_labs = NULL) {
  base_adj <- c("age","sex","score","ecog_score_cat2",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  if (!is.null(pre_labs)) base_adj <- c(base_adj, pre_labs)
  base_adj
}

fg_disc_row <- function(time_var, status_var, label, pre_labs = NULL) {
  adj <- .disc_adj_set(pre_labs)
  d <- dat %>%
    dplyr::select(all_of(c("egfr_disc_per10dec", time_var, status_var, adj))) %>%
    tidyr::drop_na()
  adj_df <- d[, adj, drop = FALSE]
  X_adj  <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X      <- cbind(egfr_disc_per10dec = d$egfr_disc_per10dec, X_adj)
  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])
  fit <- cmprsk::crr(time_num, stat_num, cov1 = X, failcode = 1)
  b <- unname(fit$coef[1]); se <- sqrt(fit$var[1, 1])
  hr <- exp(b); lcl <- exp(b - 1.96 * se); ucl <- exp(b + 1.96 * se)
  pv <- 2 * (1 - pnorm(abs(b / se)))
  tibble(
    Outcome = label,
    Model   = "Fine-Gray",
    N       = nrow(d),
    `Excluded (missing cov.)` = nrow(dat) - nrow(d),
    Events  = sum(stat_num == 1, na.rm = TRUE),
    `(sub)HR (95% CI)` = sprintf("%.2f (%.2f, %.2f)", hr, lcl, ucl),
    `p-value` = ifelse(pv < 0.001, "<0.001", sprintf("%.3f", pv))
  )
}
# Ritu: guard against unfittable sparse-outcome models.
fg_disc_row <- .wrap_row(fg_disc_row)


cox_disc_row <- function(time_var, status_var, label, pre_labs = NULL) {
  adj <- .disc_adj_set(pre_labs)
  d <- dat %>%
    dplyr::select(all_of(c("egfr_disc_per10dec", time_var, status_var, adj))) %>%
    tidyr::drop_na()
  fmla <- as.formula(paste0("Surv(", time_var, ", ", status_var,
                            ") ~ egfr_disc_per10dec + ",
                            paste(adj, collapse = " + ")))
  fit <- survival::coxph(fmla, data = d)
  b   <- unname(coef(fit)["egfr_disc_per10dec"])
  se  <- sqrt(vcov(fit)["egfr_disc_per10dec", "egfr_disc_per10dec"])
  hr  <- exp(b); lcl <- exp(b - 1.96 * se); ucl <- exp(b + 1.96 * se)
  pv  <- 2 * (1 - pnorm(abs(b / se)))
  tibble(
    Outcome = label,
    Model   = "Cox PH",
    N       = nrow(d),
    `Excluded (missing cov.)` = nrow(dat) - nrow(d),
    Events  = sum(d[[status_var]] == 1, na.rm = TRUE),
    `(sub)HR (95% CI)` = sprintf("%.2f (%.2f, %.2f)", hr, lcl, ucl),
    `p-value` = ifelse(pv < 0.001, "<0.001", sprintf("%.3f", pv))
  )
}
# Ritu: guard against unfittable sparse-outcome models.
cox_disc_row <- .wrap_row(cox_disc_row)


disc_summary <- bind_rows(
  fg_disc_row ("cmp_time_anemia_2",     "cmp_status_anemia_2",     "Anemia Grade 2",                   "pre_HGB_45days"),
  fg_disc_row ("cmp_time_anemia_3",     "cmp_status_anemia_3",     "Anemia Grade 3",                   "pre_HGB_45days"),
  fg_disc_row ("cmp_time_throm_2",      "cmp_status_throm_2",      "Thrombocytopenia Grade 2",         "pre_PLT_45days"),
  fg_disc_row ("cmp_time_throm_3",      "cmp_status_throm_3",      "Thrombocytopenia Grade 3",         "pre_PLT_45days"),
  fg_disc_row ("cmp_time_aki_2",        "cmp_status_aki_2",        "AKI Grade 2"),
  fg_disc_row ("cmp_time_aki_kdigo",    "cmp_status_aki_kdigo",    "AKI (KDIGO)"),
  fg_disc_row ("cmp_time_grade_2_aes",  "cmp_status_grade_2_aes",  "Composite Grade 2 AEs"),
  fg_disc_row ("cmp_time_grade_3_aes",  "cmp_status_grade_3_aes",  "Composite Grade 3 AEs"),
  fg_disc_row ("cmp_time_any_hosp",     "cmp_status_any_hosp",     "Overall Hospitalization"),
  fg_disc_row ("cmp_time_side_effect",  "cmp_status_side_effect",  "Platinum-Related Hospitalization"),
  cox_disc_row("time_to_death_90",      "death_90",                "90-Day Death")
)

ft_disc <- flextable::flextable(disc_summary) |>
  flextable::set_caption("Multivariable (sub)HR per 10 mL/min decline in eGFR discrepancy (CKD-EPI Cr-Cys − Cockcroft-Gault) — Carboplatin AUC ≥ 3 cohort. Fine-Gray for competing-risk outcomes; Cox PH for 90-day death.") |>
  flextable::autofit()
flextable::save_as_docx(ft_disc,
  path = file.path(docx_dir, "sec10_disc_summary.docx"))
ft_disc
```
```{r}
#| label: ritu-auc3-linsubhr-disc-egfr-helper
plot_subhr_linear_egfrdisc <- function(time_var, status_var, extra_adj = NULL,
                                       outcome_label, n_bonf = 6) {
  base_adj <- c("age","sex","score","ecog_score_cat2",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  keep <- c("egfr_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_discrepancy = d$egfr_discrepancy, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]
  se_b   <- sqrt(V_beta)

  q1    <- as.numeric(quantile(d$egfr_discrepancy, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_discrepancy, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  hr10  <- exp(-10 * beta);       hr10_l <- exp(-10 * beta - 1.96 * 10 * se_b);     hr10_u <- exp(-10 * beta + 1.96 * 10 * se_b)
  hri   <- exp(-iqr_w * beta);    hri_l <- exp(-iqr_w * beta - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(-iqr_w * beta + 1.96 * abs(iqr_w) * se_b)
  pval  <- 2 * (1 - pnorm(abs(beta / se_b)))
  pval_bonf <- min(pval * n_bonf, 1)
  p_shown <- if (n_bonf > 1) pval_bonf else pval
  p_lbl   <- if (n_bonf > 1) sprintf("p_Bonf = %s (n = %d)", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)), n_bonf) else sprintf("p = %s", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)))
  subtitle_str <- sprintf(
    "subHR per 10 mL/min decline: %.2f (%.2f-%.2f), %s  |  per IQR decline (Δ = %.1f): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f]",
    hr10, hr10_l, hr10_u, p_lbl, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$egfr_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    geom_vline(xintercept = c(q1, q3), linetype = "dashed",
               color = "steelblue", alpha = 0.7) +
    labs(x = "eGFR Discrepancy (mL/min)",
         y = "subHR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25"))
}
# Ritu: guard against unfittable sparse-outcome models.
plot_subhr_linear_egfrdisc <- .wrap_plot(plot_subhr_linear_egfrdisc)


plot_cox_linear_egfrdisc <- function(time_var, status_var, extra_adj = NULL,
                                     outcome_label, n_bonf = 6) {
  base_adj <- c("age","sex","score","ecog_score_cat2",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  keep <- c("egfr_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ egfr_discrepancy + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- survival::coxph(fmla, data = d)

  beta   <- coef(fit)["egfr_discrepancy"]
  V_beta <- vcov(fit)["egfr_discrepancy", "egfr_discrepancy"]
  se_b   <- sqrt(V_beta)

  q1    <- as.numeric(quantile(d$egfr_discrepancy, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_discrepancy, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  hr10  <- exp(-10 * beta);       hr10_l <- exp(-10 * beta - 1.96 * 10 * se_b);     hr10_u <- exp(-10 * beta + 1.96 * 10 * se_b)
  hri   <- exp(-iqr_w * beta);    hri_l <- exp(-iqr_w * beta - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(-iqr_w * beta + 1.96 * abs(iqr_w) * se_b)
  pval  <- 2 * (1 - pnorm(abs(beta / se_b)))
  pval_bonf <- min(pval * n_bonf, 1)
  p_shown <- if (n_bonf > 1) pval_bonf else pval
  p_lbl   <- if (n_bonf > 1) sprintf("p_Bonf = %s (n = %d)", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)), n_bonf) else sprintf("p = %s", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)))
  subtitle_str <- sprintf(
    "HR per 10 mL/min decline: %.2f (%.2f-%.2f), %s  |  per IQR decline (Δ = %.1f): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f]",
    hr10, hr10_l, hr10_u, p_lbl, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$egfr_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x   = grid_x,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    geom_vline(xintercept = c(q1, q3), linetype = "dashed",
               color = "steelblue", alpha = 0.7) +
    labs(x = "eGFR Discrepancy (mL/min)",
         y = "HR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25"))
}
# Ritu: guard against unfittable sparse-outcome models.
plot_cox_linear_egfrdisc <- .wrap_plot(plot_cox_linear_egfrdisc)

```

## 9.1 Anemia Grade 2

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_anemia_2", "cmp_status_anemia_2",
                           "pre_HGB_45days", "Anemia Grade 2 (Carboplatin AUC ≥ 3)")
```

## 9.2 Anemia Grade 3

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_anemia_3", "cmp_status_anemia_3",
                           "pre_HGB_45days", "Anemia Grade 3 (Carboplatin AUC ≥ 3)")
```

## 9.3 Thrombocytopenia Grade 2

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_throm_2", "cmp_status_throm_2",
                           "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin AUC ≥ 3)")
```

## 9.4 Thrombocytopenia Grade 3

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_throm_3", "cmp_status_throm_3",
                           "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin AUC ≥ 3)")
```

## 9.5 AKI Grade 2

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_aki_2", "cmp_status_aki_2",
                           NULL, "AKI Grade 2 (Carboplatin AUC ≥ 3)")
```

## 9.6 AKI (KDIGO)

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                           NULL, "AKI (KDIGO) (Carboplatin AUC ≥ 3)")
```

## 9.7 Composite Grade 2 AEs

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                           NULL, "Composite Grade 2 AEs (Carboplatin AUC ≥ 3)")
```

## 9.8 Composite Grade 3 AEs

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                           NULL, "Composite Grade 3 AEs (Carboplatin AUC ≥ 3)")
```

## 9.9 Overall Hospitalization

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_any_hosp", "cmp_status_any_hosp",
                           NULL, "Overall Hospitalization (Carboplatin AUC ≥ 3)")
```

## 9.10 Platinum-Related Hospitalization

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_egfrdisc("cmp_time_side_effect", "cmp_status_side_effect",
                           NULL, "Platinum-Related Hospitalization (Carboplatin AUC ≥ 3)")
```

## 9.11 90-Day Death (Cox PH)

```{r}
#| label: ritu-auc3-linsubhr-egfrdisc-death
#| fig-width: 6
#| fig-height: 4
plot_cox_linear_egfrdisc("time_to_death_90", "death_90",
                         NULL, "90-Day Death (Cox PH) (Carboplatin AUC ≥ 3)")
```

# 11 Linear subHR Curves — Dose Discrepancy (raw scale) (Carboplatin AUC ≥ 3)

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-helper
plot_subhr_linear <- function(time_var, status_var, extra_adj = NULL,
                              outcome_label) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  keep <- c("dose_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(dose_discrepancy = d$dose_discrepancy, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]

  ref_x  <- median(d$dose_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$dose_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$dose_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "Dose Discrepancy (mg)",
         y = "subHR (95% CI)",
         title = outcome_label) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11)
}
# Ritu: guard against unfittable sparse-outcome models.
plot_subhr_linear <- .wrap_plot(plot_subhr_linear)


plot_cox_linear <- function(time_var, status_var, extra_adj = NULL,
                            outcome_label) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  keep <- c("dose_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ dose_discrepancy + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- survival::coxph(fmla, data = d)

  beta   <- coef(fit)["dose_discrepancy"]
  V_beta <- vcov(fit)["dose_discrepancy", "dose_discrepancy"]

  ref_x  <- median(d$dose_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$dose_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$dose_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x   = grid_x,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "Dose Discrepancy (mg)",
         y = "HR (95% CI)",
         title = outcome_label) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11)
}
# Ritu: guard against unfittable sparse-outcome models.
plot_cox_linear <- .wrap_plot(plot_cox_linear)

```

## 10.1 Anemia Grade 2

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_2", "cmp_status_anemia_2",
                  "pre_HGB_45days", "Anemia Grade 2 (Carboplatin AUC ≥ 3)")
```

## 10.2 Anemia Grade 3

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_3", "cmp_status_anemia_3",
                  "pre_HGB_45days", "Anemia Grade 3 (Carboplatin AUC ≥ 3)")
```

## 10.3 Thrombocytopenia Grade 2

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_2", "cmp_status_throm_2",
                  "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin AUC ≥ 3)")
```

## 10.4 Thrombocytopenia Grade 3

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_3", "cmp_status_throm_3",
                  "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin AUC ≥ 3)")
```

## 10.5 AKI Grade 2

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_2", "cmp_status_aki_2",
                  NULL, "AKI Grade 2 (Carboplatin AUC ≥ 3)")
```

## 10.6 AKI (KDIGO)

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                  NULL, "AKI (KDIGO) (Carboplatin AUC ≥ 3)")
```

## 10.7 Composite Grade 2 AEs

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                  NULL, "Composite Grade 2 AEs (Carboplatin AUC ≥ 3)")
```

## 10.8 Composite Grade 3 AEs

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                  NULL, "Composite Grade 3 AEs (Carboplatin AUC ≥ 3)")
```

## 10.9 Overall Hospitalization

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_any_hosp", "cmp_status_any_hosp",
                  NULL, "Overall Hospitalization (Carboplatin AUC ≥ 3)")
```

## 10.10 Platinum-Related Hospitalization

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_side_effect", "cmp_status_side_effect",
                  NULL, "Platinum-Related Hospitalization (Carboplatin AUC ≥ 3)")
```

## 10.11 90-Day Death (Cox PH)

```{r}
#| label: ritu-auc3-linsubhr-dosedisc-death
#| fig-width: 6
#| fig-height: 4
plot_cox_linear("time_to_death_90", "death_90",
                NULL, "90-Day Death (Cox PH) (Carboplatin AUC ≥ 3)")
```

# 12 Linear subHR Curves — Hospitalization by Reason (Carboplatin AUC ≥ 3)

## 12.1 Nausea/Vomiting/GI

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp1
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_1", "cmp_status_hosp_1",
                        NULL, "Nausea/Vomiting/GI (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

## 12.2 Failure to Thrive/Fatigue/Dehydration

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp2
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_2", "cmp_status_hosp_2",
                        NULL, "Failure to Thrive/Fatigue/Dehydration (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

## 12.3 AKI

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp3
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_3", "cmp_status_hosp_3",
                        NULL, "AKI (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

## 12.4 Electrolyte Abnormalities

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp4
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_4", "cmp_status_hosp_4",
                        NULL, "Electrolyte Abnormalities (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

## 12.5 Cytopenia

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp5
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_5", "cmp_status_hosp_5",
                        NULL, "Cytopenia (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

## 12.6 Febrile Neutropenia

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp6
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_6", "cmp_status_hosp_6",
                        NULL, "Febrile Neutropenia (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

## 12.7 Infection/Sepsis

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp7
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_7", "cmp_status_hosp_7",
                        NULL, "Infection/Sepsis (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

## 12.8 Cancer Progression

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp8
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_8", "cmp_status_hosp_8",
                        NULL, "Cancer Progression (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

## 12.9 Immune-related AE & Other

Composite competing-risk outcome combining hospitalisations coded as Immune-related AE (reason 9) and Other (reason 11). Event = 1 if either occurred within 90 days; time = earliest of the two.

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp-immune-other
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_immune_other", "cmp_status_hosp_immune_other",
                        NULL, "Immune-related AE & Other (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

## 12.10 Planned Surgery/Port

```{r}
#| label: ritu-auc3-linsubhr-ratio-hosp10
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_ratio("cmp_time_hosp_10", "cmp_status_hosp_10",
                        NULL, "Planned Surgery/Port (Carboplatin AUC ≥ 3)", n_bonf = 1)
```

# 13 Scatter Plots — Dose Discrepancy vs eGFR (Carboplatin AUC ≥ 3)

## 13.1 Dose Discrepancy vs CKD-EPI Cr-Cys (unindexed)

```{r}
#| label: ritu-auc3-scatter-epi
#| fig-width: 6
#| fig-height: 4
ggplot(dat %>% filter(!is.na(dose_discrepancy)),
       aes(x = ckd_epi_gfr_cre_cys_unindex, y = dose_discrepancy)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, color = "steelblue") +
  labs(x = "CKD-EPI Cr-Cys eGFR (unindexed, mL/min)",
       y = "Dose Discrepancy (mg)",
       title = "Dose Discrepancy vs CKD-EPI Cr-Cys eGFR (Carboplatin AUC ≥ 3)") +
  theme_minimal(base_size = 11)
```

## 13.2 Dose Discrepancy vs Cockcroft-Gault

```{r}
#| label: ritu-auc3-scatter-cg
#| fig-width: 6
#| fig-height: 4
ggplot(dat %>% filter(!is.na(dose_discrepancy)),
       aes(x = cockcroft, y = dose_discrepancy)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, color = "steelblue") +
  labs(x = "Cockcroft-Gault eGFR (mL/min)",
       y = "Dose Discrepancy (mg)",
       title = "Dose Discrepancy vs Cockcroft-Gault eGFR (Carboplatin AUC ≥ 3)") +
  theme_minimal(base_size = 11)
```


# 14 Adjusted CIF — Dose Discrepancy >= +25 mg (Carboplatin AUC ≥ 3)

Standardized cumulative incidence functions for each competing-risk outcome, contrasting patients with `dose_discrepancy >= 25` (red) against those with `dose_discrepancy < 25` (blue). The Fine-Gray model is fit with the binary exposure plus the same adjuster set used in Section 7. Curves are *adjusted (standardized)* via g-computation: for every patient, predict CIF under exposure = 1 and under exposure = 0, then average the two CIF curves over the cohort. Y-axis is cumulative incidence, x-axis is days from baseline.

90-day death (Section 14.11) is modelled with Cox PH instead of Fine-Gray (no competing event), and the standardized cumulative-incidence-of-death curve is `1 − S(t|Xᵢ)` averaged across the cohort.

```{r}
#| label: ritu-auc3-adjcif-helper
adj_cif <- function(time_var, status_var, extra_pre = NULL, label) {
  base_adj <- c("age","sex","score","ecog_score_cat2",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid","cockcroft")
  vars <- c("dose_discrep_ge25", base_adj, extra_pre)
  d <- dat %>%
    dplyr::select(all_of(c(time_var, status_var, vars))) %>%
    tidyr::drop_na()

  fmla <- as.formula(paste("~",
            paste(c("dose_discrep_ge25", base_adj, extra_pre), collapse = " + ")))
  X_full <- model.matrix(fmla, data = d)[, -1, drop = FALSE]

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X_full, failcode = 1)

  # subHR (95% CI) for the binary exposure, extracted from the same FG fit
  # dose_discrep_ge25 is the first column of cov1 (entered first in the formula)
  beta_e <- unname(fit$coef[1])
  se_e   <- sqrt(fit$var[1, 1])
  hr     <- exp(beta_e)
  lcl    <- exp(beta_e - 1.96 * se_e)
  ucl    <- exp(beta_e + 1.96 * se_e)
  pval   <- 2 * (1 - pnorm(abs(beta_e / se_e)))
  p_str  <- ifelse(pval < 0.001, "<0.001", sprintf("%.3f", pval))
  subtitle_str <- sprintf(
    "Discrep >= +25 vs <+25: subHR = %.2f (95%% CI %.2f-%.2f), p = %s",
    hr, lcl, ucl, p_str
  )

  X0 <- X_full; X0[, "dose_discrep_ge25"] <- 0
  X1 <- X_full; X1[, "dose_discrep_ge25"] <- 1

  pred0 <- predict(fit, X0)
  pred1 <- predict(fit, X1)

  times <- pred0[, 1]
  cif0  <- rowMeans(pred0[, -1, drop = FALSE])
  cif1  <- rowMeans(pred1[, -1, drop = FALSE])

  df <- bind_rows(
    tibble(time = times, cif = cif0, group = "Discrep < +25 mg"),
    tibble(time = times, cif = cif1, group = "Discrep >= +25 mg")
  )

  ymax <- max(df$cif, na.rm = TRUE)

  ggplot(df, aes(x = time, y = cif, color = group)) +
    geom_step(linewidth = 1) +
    scale_color_manual(values = c("Discrep < +25 mg"  = "#1F78B4",
                                  "Discrep >= +25 mg" = "#E31A1C")) +
    coord_cartesian(ylim = c(0, max(0.05, ymax * 1.05))) +
    labs(x = "Days from baseline",
         y = "Cumulative incidence",
         color = NULL,
         title = label,
         subtitle = subtitle_str) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "top",
          plot.subtitle = element_text(size = 10, color = "grey25"))
}
# Ritu: guard against unfittable sparse-outcome models.
adj_cif <- .wrap_plot(adj_cif)


adj_death_curve <- function(time_var = "time_to_death_90",
                            status_var = "death_90", label) {
  base_adj <- c("age","sex","score","ecog_score_cat2",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid","cockcroft")
  vars <- c("dose_discrep_ge25", base_adj)
  d <- dat %>%
    dplyr::select(all_of(c(time_var, status_var, vars))) %>%
    tidyr::drop_na()

  rhs <- paste(c("dose_discrep_ge25", base_adj), collapse = " + ")
  fmla <- as.formula(sprintf("survival::Surv(%s, %s) ~ %s",
                             time_var, status_var, rhs))
  fit <- survival::coxph(fmla, data = d)

  beta_e <- unname(coef(fit)["dose_discrep_ge25"])
  se_e   <- sqrt(vcov(fit)["dose_discrep_ge25", "dose_discrep_ge25"])
  hr     <- exp(beta_e)
  lcl    <- exp(beta_e - 1.96 * se_e)
  ucl    <- exp(beta_e + 1.96 * se_e)
  pval   <- 2 * (1 - pnorm(abs(beta_e / se_e)))
  p_str  <- ifelse(pval < 0.001, "<0.001", sprintf("%.3f", pval))
  subtitle_str <- sprintf(
    "Discrep >= +25 vs <+25: HR = %.2f (95%% CI %.2f-%.2f), p = %s   (Cox PH)",
    hr, lcl, ucl, p_str
  )

  d0 <- d; d0$dose_discrep_ge25 <- 0
  d1 <- d; d1$dose_discrep_ge25 <- 1

  sf0 <- survival::survfit(fit, newdata = d0)
  sf1 <- survival::survfit(fit, newdata = d1)

  s0 <- if (is.matrix(sf0$surv)) sf0$surv else as.matrix(sf0$surv)
  s1 <- if (is.matrix(sf1$surv)) sf1$surv else as.matrix(sf1$surv)

  cif0 <- 1 - rowMeans(s0)
  cif1 <- 1 - rowMeans(s1)

  df <- bind_rows(
    tibble(time = sf0$time, cif = cif0, group = "Discrep < +25 mg"),
    tibble(time = sf1$time, cif = cif1, group = "Discrep >= +25 mg")
  )

  ymax <- max(df$cif, na.rm = TRUE)

  ggplot(df, aes(x = time, y = cif, color = group)) +
    geom_step(linewidth = 1) +
    scale_color_manual(values = c("Discrep < +25 mg"  = "#1F78B4",
                                  "Discrep >= +25 mg" = "#E31A1C")) +
    coord_cartesian(ylim = c(0, max(0.05, ymax * 1.05))) +
    labs(x = "Days from baseline",
         y = "Cumulative incidence (1 - S)",
         color = NULL,
         title = label,
         subtitle = subtitle_str) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "top",
          plot.subtitle = element_text(size = 10, color = "grey25"))
}
# Ritu: guard against unfittable sparse-outcome models.
adj_death_curve <- .wrap_plot(adj_death_curve)

```

## 14.1 Anemia Grade 2

```{r}
#| label: ritu-auc3-adjcif-anemia2
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_anemia_2", "cmp_status_anemia_2",
        "pre_HGB_45days", "Anemia Grade 2")
```

## 14.2 Anemia Grade 3

```{r}
#| label: ritu-auc3-adjcif-anemia3
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_anemia_3", "cmp_status_anemia_3",
        "pre_HGB_45days", "Anemia Grade 3")
```

## 14.3 Thrombocytopenia Grade 2

```{r}
#| label: ritu-auc3-adjcif-throm2
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_throm_2", "cmp_status_throm_2",
        "pre_PLT_45days", "Thrombocytopenia Grade 2")
```

## 14.4 Thrombocytopenia Grade 3

```{r}
#| label: ritu-auc3-adjcif-throm3
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_throm_3", "cmp_status_throm_3",
        "pre_PLT_45days", "Thrombocytopenia Grade 3")
```

## 14.5 AKI Grade 2

```{r}
#| label: ritu-auc3-adjcif-aki2
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_aki_2", "cmp_status_aki_2",
        NULL, "AKI Grade 2")
```

## 14.6 AKI (KDIGO)

```{r}
#| label: ritu-auc3-adjcif-akikdigo
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
        NULL, "AKI (KDIGO)")
```

## 14.7 Composite Grade 2 AEs

```{r}
#| label: ritu-auc3-adjcif-grade2
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
        NULL, "Composite Grade 2 AEs")
```

## 14.8 Composite Grade 3 AEs

```{r}
#| label: ritu-auc3-adjcif-grade3
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
        NULL, "Composite Grade 3 AEs")
```

## 14.9 Overall Hospitalization

```{r}
#| label: ritu-auc3-adjcif-anyhosp
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_any_hosp", "cmp_status_any_hosp",
        NULL, "Overall Hospitalization")
```

## 14.10 Platinum-Related Hospitalization

```{r}
#| label: ritu-auc3-adjcif-sideeffect
#| fig-width: 7
#| fig-height: 4
adj_cif("cmp_time_side_effect", "cmp_status_side_effect",
        NULL, "Platinum-Related Hospitalization")
```

## 14.11 90-Day Death (Cox PH)

```{r}
#| label: ritu-auc3-adjcif-death
#| fig-width: 7
#| fig-height: 4
adj_death_curve("time_to_death_90", "death_90", "90-Day Death")
```

# 15 Paper

```{r}
#| label: ritu-auc3-paper-stats
#| include: false
n_excess  <- sum(dat$dose_discrep_ge25 == 1, na.rm = TRUE)
n_with_dx <- sum(!is.na(dat$dose_discrepancy))
pct_excess <- round(n_excess / n_with_dx * 100, 1)
```

A total of `r n_excess` (`r pct_excess`%) patients received an excess dose of carboplatin, defined as ≥ 25 mg higher than the dose that would have been predicted using the CKD-EPI eGFR~CR-CYS~ equation adjusted for actual BSA.

(Denominator: `r n_with_dx` carboplatin AUC ≥ 3 patients with a computable predicted dose.)

# 16 Sensitivity Analysis — eGFR Difference (%) — (CKD-EPI 2012 CysC − CKD-EPI 2021 Cr) / CKD-EPI 2021 Cr, per 10 % decline (Carboplatin AUC ≥ 3)

Sensitivity analysis using an alternative eGFR-difference (%) definition for the linear exposure:

- **Numerator**: eGFR<sub>CYS</sub> − eGFR<sub>CR</sub>, where eGFR<sub>CYS</sub> = CKD-EPI **2012** cystatin C-only (`baseline_cys_c_egfr_unindexed`) and eGFR<sub>CR</sub> = CKD-EPI **2021** race-free creatinine-only (`baseline_cre_egfr_unindexed`).
- **Denominator**: eGFR<sub>CR</sub>.
- Percent difference: `egfr_diff_pct_sens = 100 * (baseline_cys_c_egfr_unindexed - baseline_cre_egfr_unindexed) / baseline_cre_egfr_unindexed`.

One row per outcome. Multivariable Fine-Gray model fit with `egfr_diff_pct_sens_per10 = -egfr_diff_pct_sens / 10` plus the same adjuster set as Section 5 (no `platin_group` in the AUC ≥ 3 cohort). The HR for this variable reads as the multiplicative subHR per **10 % decline** in sensitivity eGFR difference. 90-day death uses Cox PH. p-values in this summary table are **raw Wald** (not Bonferroni-adjusted); the plot subtitles in Sections 16.1–16.11 apply Bonferroni correction across the six primary AE outcomes.

[📄 Download Word table](../tables/auc3/sec16_egfr_ratio_sens_summary.docx)

```{r}
#| label: ritu-auc3-fg-sens-ratio-summary
.sens_adj_set <- function(pre_labs = NULL) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  if (!is.null(pre_labs)) base_adj <- c(base_adj, pre_labs)
  base_adj
}

fg_sens_row <- function(time_var, status_var, label, pre_labs = NULL) {
  adj <- .sens_adj_set(pre_labs)
  d <- dat %>%
    dplyr::select(all_of(c("egfr_diff_pct_sens_per10", time_var, status_var, adj))) %>%
    tidyr::drop_na()
  adj_df <- d[, adj, drop = FALSE]
  X_adj  <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X      <- cbind(egfr_diff_pct_sens_per10 = d$egfr_diff_pct_sens_per10, X_adj)
  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])
  fit <- cmprsk::crr(time_num, stat_num, cov1 = X, failcode = 1)
  b <- unname(fit$coef[1]); se <- sqrt(fit$var[1, 1])
  hr <- exp(b); lcl <- exp(b - 1.96 * se); ucl <- exp(b + 1.96 * se)
  pv <- 2 * (1 - pnorm(abs(b / se)))
  tibble(
    Outcome = label,
    Model   = "Fine-Gray",
    N       = nrow(d),
    `Excluded (missing cov.)` = nrow(dat) - nrow(d),
    Events  = sum(stat_num == 1, na.rm = TRUE),
    `(sub)HR (95% CI)` = sprintf("%.2f (%.2f, %.2f)", hr, lcl, ucl),
    `p-value` = ifelse(pv < 0.001, "<0.001", sprintf("%.3f", pv))
  )
}
# Ritu: guard against unfittable sparse-outcome models.
fg_sens_row <- .wrap_row(fg_sens_row)


cox_sens_row <- function(time_var, status_var, label, pre_labs = NULL) {
  adj <- .sens_adj_set(pre_labs)
  d <- dat %>%
    dplyr::select(all_of(c("egfr_diff_pct_sens_per10", time_var, status_var, adj))) %>%
    tidyr::drop_na()
  fmla <- as.formula(paste0("Surv(", time_var, ", ", status_var,
                            ") ~ egfr_diff_pct_sens_per10 + ",
                            paste(adj, collapse = " + ")))
  fit <- survival::coxph(fmla, data = d)
  b   <- unname(coef(fit)["egfr_diff_pct_sens_per10"])
  se  <- sqrt(vcov(fit)["egfr_diff_pct_sens_per10", "egfr_diff_pct_sens_per10"])
  hr  <- exp(b); lcl <- exp(b - 1.96 * se); ucl <- exp(b + 1.96 * se)
  pv  <- 2 * (1 - pnorm(abs(b / se)))
  tibble(
    Outcome = label,
    Model   = "Cox PH",
    N       = nrow(d),
    `Excluded (missing cov.)` = nrow(dat) - nrow(d),
    Events  = sum(d[[status_var]] == 1, na.rm = TRUE),
    `(sub)HR (95% CI)` = sprintf("%.2f (%.2f, %.2f)", hr, lcl, ucl),
    `p-value` = ifelse(pv < 0.001, "<0.001", sprintf("%.3f", pv))
  )
}
# Ritu: guard against unfittable sparse-outcome models.
cox_sens_row <- .wrap_row(cox_sens_row)


sens_summary <- bind_rows(
  fg_sens_row ("cmp_time_anemia_2",     "cmp_status_anemia_2",     "Anemia Grade 2",                   "pre_HGB_45days"),
  fg_sens_row ("cmp_time_anemia_3",     "cmp_status_anemia_3",     "Anemia Grade 3",                   "pre_HGB_45days"),
  fg_sens_row ("cmp_time_throm_2",      "cmp_status_throm_2",      "Thrombocytopenia Grade 2",         "pre_PLT_45days"),
  fg_sens_row ("cmp_time_throm_3",      "cmp_status_throm_3",      "Thrombocytopenia Grade 3",         "pre_PLT_45days"),
  fg_sens_row ("cmp_time_aki_2",        "cmp_status_aki_2",        "AKI Grade 2"),
  fg_sens_row ("cmp_time_aki_kdigo",    "cmp_status_aki_kdigo",    "AKI (KDIGO)"),
  fg_sens_row ("cmp_time_grade_2_aes",  "cmp_status_grade_2_aes",  "Composite Grade 2 AEs"),
  fg_sens_row ("cmp_time_grade_3_aes",  "cmp_status_grade_3_aes",  "Composite Grade 3 AEs"),
  fg_sens_row ("cmp_time_any_hosp",     "cmp_status_any_hosp",     "Overall Hospitalization"),
  fg_sens_row ("cmp_time_side_effect",  "cmp_status_side_effect",  "Platinum-Related Hospitalization"),
  cox_sens_row("time_to_death_90",      "death_90",                "90-Day Death")
)

ft_sens <- flextable::flextable(sens_summary) |>
  flextable::set_caption("Sensitivity analysis: multivariable (sub)HR per 10 % decline in eGFR difference (%) — 100 × (CKD-EPI 2012 CysC − CKD-EPI 2021 Cr) / CKD-EPI 2021 Cr — Carboplatin AUC ≥ 3 cohort. Fine-Gray for competing-risk outcomes; Cox PH for 90-day death.") |>
  flextable::autofit()
flextable::save_as_docx(ft_sens,
  path = file.path(docx_dir, "sec16_egfr_ratio_sens_summary.docx"))
ft_sens
```

```{r}
#| label: ritu-auc3-linsubhr-sens-helper
plot_subhr_linear_sens <- function(time_var, status_var, extra_adj = NULL,
                                   outcome_label, n_bonf = 6) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  keep <- c("egfr_diff_pct_sens", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_diff_pct_sens = d$egfr_diff_pct_sens, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]
  se_b   <- sqrt(V_beta)

  q1    <- as.numeric(quantile(d$egfr_diff_pct_sens, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_diff_pct_sens, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  hr10  <- exp(-10 * beta);     hr10_l <- exp(-10 * beta - 1.96 * 10 * se_b);   hr10_u <- exp(-10 * beta + 1.96 * 10 * se_b)
  hri   <- exp(-iqr_w * beta);   hri_l  <- exp(-iqr_w * beta - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(-iqr_w * beta + 1.96 * abs(iqr_w) * se_b)
  pval  <- 2 * (1 - pnorm(abs(beta / se_b)))
  pval_bonf <- min(pval * n_bonf, 1)
  p_shown <- if (n_bonf > 1) pval_bonf else pval
  p_lbl   <- if (n_bonf > 1) sprintf("p_Bonf = %s (n = %d)", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)), n_bonf) else sprintf("p = %s", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)))
  subtitle_str <- sprintf(
    "subHR per 10 %% decline: %.2f (%.2f-%.2f), %s  |  per IQR decline (Δ = %.1f %%): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f] %%",
    hr10, hr10_l, hr10_u, p_lbl, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_diff_pct_sens, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_diff_pct_sens, 0.025, na.rm = TRUE),
                quantile(d$egfr_diff_pct_sens, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  p <- ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    geom_vline(xintercept = c(q1, q3), linetype = "dashed",
               color = "steelblue", alpha = 0.7) +
    labs(x = "Sensitivity eGFR Difference (%): 100 × (CKD-EPI 2012 CysC − CKD-EPI 2021 Cr) / CKD-EPI 2021 Cr",
         y = "subHR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25"))
  p_fine <- p + scale_x_continuous(breaks = seq(-100, 200, 10))
  .lbl <- tryCatch(knitr::opts_current$get("label"), error = function(e) NULL)
  if (!is.null(.lbl)) .pptx_pair[[.lbl]] <- list(default = p, fine = p_fine)
  p / p_fine
}
# Ritu: guard against unfittable sparse-outcome models.
plot_subhr_linear_sens <- .wrap_plot(plot_subhr_linear_sens)


plot_cox_linear_sens <- function(time_var, status_var, extra_adj = NULL,
                                 outcome_label, n_bonf = 6) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","thyroid")
  keep <- c("egfr_diff_pct_sens", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ egfr_diff_pct_sens + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- survival::coxph(fmla, data = d)

  beta   <- coef(fit)["egfr_diff_pct_sens"]
  V_beta <- vcov(fit)["egfr_diff_pct_sens", "egfr_diff_pct_sens"]
  se_b   <- sqrt(V_beta)

  q1    <- as.numeric(quantile(d$egfr_diff_pct_sens, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_diff_pct_sens, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  hr10  <- exp(-10 * beta);     hr10_l <- exp(-10 * beta - 1.96 * 10 * se_b);   hr10_u <- exp(-10 * beta + 1.96 * 10 * se_b)
  hri   <- exp(-iqr_w * beta);   hri_l  <- exp(-iqr_w * beta - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(-iqr_w * beta + 1.96 * abs(iqr_w) * se_b)
  pval  <- 2 * (1 - pnorm(abs(beta / se_b)))
  pval_bonf <- min(pval * n_bonf, 1)
  p_shown <- if (n_bonf > 1) pval_bonf else pval
  p_lbl   <- if (n_bonf > 1) sprintf("p_Bonf = %s (n = %d)", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)), n_bonf) else sprintf("p = %s", ifelse(p_shown < 0.001, "<0.001", sprintf("%.3f", p_shown)))
  subtitle_str <- sprintf(
    "HR per 10 %% decline: %.2f (%.2f-%.2f), %s  |  per IQR decline (Δ = %.1f %%): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f] %%",
    hr10, hr10_l, hr10_u, p_lbl, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_diff_pct_sens, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_diff_pct_sens, 0.025, na.rm = TRUE),
                quantile(d$egfr_diff_pct_sens, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x   = grid_x,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  p <- ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    geom_vline(xintercept = c(q1, q3), linetype = "dashed",
               color = "steelblue", alpha = 0.7) +
    labs(x = "Sensitivity eGFR Difference (%): 100 × (CKD-EPI 2012 CysC − CKD-EPI 2021 Cr) / CKD-EPI 2021 Cr",
         y = "HR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25"))
  p_fine <- p + scale_x_continuous(breaks = seq(-100, 200, 10))
  .lbl <- tryCatch(knitr::opts_current$get("label"), error = function(e) NULL)
  if (!is.null(.lbl)) .pptx_pair[[.lbl]] <- list(default = p, fine = p_fine)
  p / p_fine
}
# Ritu: guard against unfittable sparse-outcome models.
plot_cox_linear_sens <- .wrap_plot(plot_cox_linear_sens)

```

## 16.1 Anemia Grade 2

```{r}
#| label: ritu-auc3-linsubhr-sens-anemia2
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_anemia_2", "cmp_status_anemia_2",
                       "pre_HGB_45days", "Anemia Grade 2 (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.2 Anemia Grade 3

```{r}
#| label: ritu-auc3-linsubhr-sens-anemia3
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_anemia_3", "cmp_status_anemia_3",
                       "pre_HGB_45days", "Anemia Grade 3 (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.3 Thrombocytopenia Grade 2

```{r}
#| label: ritu-auc3-linsubhr-sens-throm2
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_throm_2", "cmp_status_throm_2",
                       "pre_PLT_45days", "Thrombocytopenia Grade 2 (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.4 Thrombocytopenia Grade 3

```{r}
#| label: ritu-auc3-linsubhr-sens-throm3
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_throm_3", "cmp_status_throm_3",
                       "pre_PLT_45days", "Thrombocytopenia Grade 3 (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.5 AKI Grade 2

```{r}
#| label: ritu-auc3-linsubhr-sens-aki2
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_aki_2", "cmp_status_aki_2",
                       NULL, "AKI Grade 2 (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.6 AKI (KDIGO)

```{r}
#| label: ritu-auc3-linsubhr-sens-akikdigo
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                       NULL, "AKI (KDIGO) (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.7 Composite Grade 2 AEs

```{r}
#| label: ritu-auc3-linsubhr-sens-grade2
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                       NULL, "Composite Grade 2 AEs (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.8 Composite Grade 3 AEs

```{r}
#| label: ritu-auc3-linsubhr-sens-grade3
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                       NULL, "Composite Grade 3 AEs (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.9 Overall Hospitalization

```{r}
#| label: ritu-auc3-linsubhr-sens-anyhosp
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_any_hosp", "cmp_status_any_hosp",
                       NULL, "Overall Hospitalization (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.10 Platinum-Related Hospitalization

```{r}
#| label: ritu-auc3-linsubhr-sens-sideeffect
#| fig-width: 6
#| fig-height: 8
plot_subhr_linear_sens("cmp_time_side_effect", "cmp_status_side_effect",
                       NULL, "Platinum-Related Hospitalization (Sensitivity, Carboplatin AUC ≥ 3)")
```

## 16.11 90-Day Death (Cox PH)

```{r}
#| label: ritu-auc3-linsubhr-sens-death
#| fig-width: 6
#| fig-height: 8
plot_cox_linear_sens("time_to_death_90", "death_90",
                     NULL, "90-Day Death (Cox PH) (Sensitivity, Carboplatin AUC ≥ 3)")
```
